---
title: "Gamma Lot QC"
author: "Dilsher Singh Dhillon"
date: "`r format(Sys.time(),'%d %B,%Y')`"
output:
  html_document:
    toc: true
    toc_float : true 
---
<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: #948DFF;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r}
library(tidyverse)
library(plotly)
freenome_colors <- c('#948DFF', '#1DE3FE', '#BBD532', '#FF9D42',  '#FC2E7B', 
                   '#FECDD1')
```


Use these PATE functions to process the data from GCS 
```{r eval=FALSE, echo=TRUE}
pate-rnd xmap-collector --include_file_str QC_Gamma \
--out_file_name gamma_qc.csv
```

Use this to import the data into JH from GCS 

```{r eval=FALSE, echo=TRUE}
gsutil cp gs://inhouse-xmap-data/user_data_frames/gamma_qc.csv
/home/ddhillon/projects/beta-av-testing/data/raw/gamma_qc.csv
```

## Introduction 

This is a one off quick check experiment to make sure everything looks ok 

[benchling](https://freenome.benchling.com/freenome/f/lib_WUAAbbjQ-08-rds-gamma-lot/etr_ym83fKf2-jntmwz-rds-gamma-lot-functional-qc/edit) 


```{r}
raw <- readr::read_csv(here::here("data", "raw", "gamma_qc.csv"), 
                       show_col_types = FALSE)
```

There are two runs for panel 2 - why? this is because one of the QCs for the march 3rd run was switched and Jinesh and Wilson changed the platemap and re-ran the *software* 

We will only use the 7th march data since it has the correct positioning  


```{r}
raw %>% 
  count(file_name)
```


```{r}
## take data only for the 7 markers   
raw <- raw %>% 
  filter(assay %in% c("CEACAM5", "WFDC2", "FLT3L", "TNC", "IL1R2", "CXCL8", "MUC16")) %>% 
  mutate(assay = ifelse(assay == "CXCL8", "IL-8", assay), 
         assay = ifelse(assay == "CEACAM5", "CEA", assay), 
         assay = ifelse(assay == "IL1R2", "IL-1 R2", assay), 
         assay = ifelse(assay == "MUC16", "MUC-16", assay)) %>% 
  filter(file_name != "20220303_QC_Gamma_Panel2_20220304_133848.csv")
```




## Analysis 

### Estimate Beta using Gamma Curve 

We take the curve fit by gamma, and then interpolate the beta standards and check the concentrations. We will then use these interpolated concentrations to see what the % recovery is, and whether it is within the expected interval we expect it to be.  

```{r}
## first, we import the beta historical data till february 22nd 
beta_historical <- readr::read_csv(here::here("data", "raw", "beta-lot-stds-controls-2022-02-22.csv"), 
                                   show_col_types = FALSE) %>% 
  filter(assay %in% c(c("CEA", "WFDC2", "FLT3L", "TNC", "IL-1 R2", "IL-8", "MUC-16"))) %>% 
  mutate(bead_fail = ifelse(bead_count < 35, 1, 0)) %>% 
  filter(bead_fail == 0) %>% ## no bead failures 
  mutate(batch = str_remove(file_name, "_[0-9]+.csv")) %>%
  filter(!grepl("20211028_Reproducibilit_Panel2_Plate3", file_name)) %>% 
  filter(sample_type == "standard") %>% 
  filter(!grepl("Salt", xponent_id))
beta_historical %>% 
  count(xponent_id, assay)
```

```{r}
beta_interpolated <- raw %>% 
  filter(grepl("Beta", xponent_id)) %>% 
  select(xponent_id, assay, calc_conc) %>% 
  group_by(xponent_id, assay) %>% 
  summarise(beta_conc_gamma = mean(calc_conc, na.rm = TRUE)) %>% 
  mutate(xponent_id = case_when(grepl("Std1", xponent_id) ~ "Standard1", 
                                grepl("Std2", xponent_id) ~ "Standard2", 
                                grepl("Std3", xponent_id) ~ "Standard3", 
                                grepl("Std4", xponent_id) ~ "Standard4", 
                                grepl("Std5", xponent_id) ~ "Standard5", 
                                grepl("Std6", xponent_id) ~ "Standard6")) %>% 
  ungroup()

beta_interpolated %>% 
  count(xponent_id, assay)
```

Now we take the `beta_interpolated` data and merge it with our historical data  

```{r}
beta_merged <- beta_historical %>% 
  select(xponent_id, assay, calc_conc, pct_recovery, batch, standard_expected_concentration) %>% 
  left_join(beta_interpolated, by = c("xponent_id", "assay")) %>% 
  mutate(beta_gamma_pct_recovery = 100*beta_conc_gamma/standard_expected_concentration)
```

```{r}
beta_merged_intervals <- beta_merged %>% 
  group_by(assay, xponent_id, batch) %>% 
  mutate(pct_recovery = mean(pct_recovery, na.rm = TRUE)) %>% 
  distinct(pct_recovery, .keep_all = TRUE) %>% 
  #summarise(pct_recovery = mean(pct_recovery, na.rm = TRUE)) %>% 
  ungroup() %>% 
  filter(pct_recovery < 1000) %>% ## there are a few edge cases which we ignore  
  group_by(xponent_id, assay) %>%
  nest() %>% 
  mutate(tol_df = map(data, ~ tolerance::normtol.int(.x$pct_recovery, 
                                                     method = "EXACT", side = 2, m = 500, 
                           log.norm = FALSE, P = 0.95))) %>% 
   unnest(cols = tol_df) %>% 
  janitor::clean_names() 
```

```{r}
p1 <- beta_merged_intervals %>% 
  unnest(cols = data) %>% 
  mutate(panel = ifelse(assay %in% c("CEA", "TNC", "WFDC2"), "panel-2", "panel-1")) %>% 
  rename(beta_lot_historical_average = x_bar) %>% 
  filter(panel == "panel-1") %>% 
  ggplot(.,aes(xponent_id, beta_lot_historical_average)) + 
  geom_point(color = freenome_colors[4]) + 
  geom_errorbar(aes(ymin = x2_sided_lower, ymax = x2_sided_upper), width = 0.25, color = freenome_colors[2]) + 
  geom_point(aes(xponent_id, beta_gamma_pct_recovery), color = freenome_colors[1]) + 
  facet_grid(cols = vars(assay)) + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "Estimated Beta Lot % Recovery using Gamma Curve(Purple)", 
       subtitle = "95 % Tolerance Intervals from Beta Lot Historical Data", 
       y = "% Recovery")

p2 <- beta_merged_intervals %>% 
  unnest(cols = data) %>% 
  mutate(panel = ifelse(assay %in% c("CEA", "TNC", "WFDC2"), "panel-2", "panel-1")) %>% 
  rename(beta_lot_historical_average = x_bar) %>% 
  filter(panel == "panel-2") %>% 
  ggplot(.,aes(xponent_id, beta_lot_historical_average)) + 
  geom_point(color = freenome_colors[4]) + 
  geom_errorbar(aes(ymin = x2_sided_lower, ymax = x2_sided_upper), width = 0.25, color = freenome_colors[2]) + 
  geom_point(aes(xponent_id, beta_gamma_pct_recovery), color = freenome_colors[1]) + 
  facet_grid(cols = vars(assay)) + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "Estimated Beta Lot % Recovery using Gamma Curve(Purple)", 
       subtitle = "95 % Tolerance Intervals from Beta Lot Historical Data", 
       y = "% Recovery")
```

```{r}
ggplotly(p1)
ggplotly(p2)
```








```
gsutil cp /home/ddhillon/projects/beta-av-testing/notebooks/gamma-lot-qc/outputs/exp-01.html gs://freenome-user-data-ddhillon/outputs/
```





























