---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(lme4)
```

## Full Factorial   

```{r}
full_factorial <- tidyr::crossing(operator = c("A", "B", "C"), 
                                  hamilton = c("1", "2", "3"), 
                                  lot = c("ach", "fch", "fce"), 
                flexmap = c("1", "2", "3"), 
                workcell = c("1", "2")) 
```

## 24 run Design expert  
I-optimal design  

```{r}
optimal <- tibble::tribble(
                              ~lot, ~workcell, ~hamilton, ~operator, ~flexmap,
                                "FCE",         "2",         "2",         "O1",        "2",
                                "FCH",         "1",         "1",         "O2",        "2",
                                "FCH",         "2",         "2",         "O1",        "1",
                                "ACH",         "2",         "1",         "O3",        "2",
                                "FCH",         "1",         "2",         "O1",        "3",
                                "FCE",         "2",         "2",         "O1",        "2",
                                "ACH",         "1",         "2",         "O3",        "3",
                                "ACH",         "1",         "3",         "O1",        "2",
                                "ACH",         "2",         "2",         "O2",        "3",
                                "FCH",         "1",         "2",         "O3",        "2",
                                "ACH",         "1",         "3",         "O1",        "3",
                                "FCE",         "2",         "3",         "O3",        "3",
                                "FCE",         "2",         "1",         "O1",        "3",
                                "ACH",         "1",         "1",         "O1",        "1",
                                "FCE",         "1",         "3",         "O2",        "2",
                                "FCH",         "2",         "3",         "O1",        "2",
                                "FCE",         "1",         "1",         "O3",        "1",
                                "FCH",         "2",         "1",         "O2",        "3",
                                "FCE",         "1",         "2",         "O2",        "1",
                                "ACH",         "2",         "3",         "O2",        "1",
                                "FCH",         "1",         "3",         "O2",        "3",
                                "ACH",         "2",         "1",         "O3",        "2",
                                "FCH",         "2",         "3",         "O3",        "1",
                                "FCE",         "1",         "1",         "O3",        "1"
                            ) %>% 
  mutate(lot = tolower(lot), 
         operator = case_when(operator == "O1" ~ "A", 
                              operator == "O2" ~ "B", 
                              operator == "O3" ~ "C"))



optimal <- tibble::tribble(
                                             ~lot, ~workcell, ~hamilton, ~operator, ~flexmap,
                                           "FCE",  1L,  1L, "O3",  2L,
                                           "FCH",  2L,  3L, "O1",  3L,
                                           "ACH",  1L,  2L, "O1",  2L,
                                           "ACH",  1L,  3L, "O1",  1L,
                                           "ACH",  1L,  1L, "O2",  3L,
                                           "FCE",  2L,  2L, "O2",  3L,
                                           "FCH",  2L,  1L, "O1",  2L,
                                           "FCH",  1L,  2L, "O2",  1L,
                                           "FCE",  1L,  2L, "O1",  3L,
                                           "FCE",  2L,  1L, "O2",  2L,
                                           "FCE",  2L,  3L, "O2",  1L,
                                           "FCE",  1L,  2L, "O1",  3L,
                                           "FCH",  2L,  2L, "O3",  2L,
                                           "FCH",  1L,  2L, "O2",  2L,
                                           "ACH",  2L,  3L, "O2",  2L,
                                           "FCE",  2L,  1L, "O1",  1L,
                                           "FCH",  1L,  1L, "O3",  1L,
                                           "ACH",  2L,  2L, "O3",  1L,
                                           "ACH",  2L,  2L, "O3",  1L,
                                           "FCE",  1L,  3L, "O3",  2L,
                                           "FCH",  1L,  1L, "O2",  1L,
                                           "ACH",  1L,  1L, "O2",  3L,
                                           "FCH",  1L,  3L, "O3",  3L,
                                           "ACH",  2L,  1L, "O3",  3L
                                           ) %>% 
                           mutate(lot = tolower(lot), 
         operator = case_when(operator == "O1" ~ "A", 
                              operator == "O2" ~ "B", 
                              operator == "O3" ~ "C")) %>% 
  mutate_all(., ~ as.character(.x))

```


**Current design**   

```{r}
current_des <- tibble::tribble(
  ~lot, ~hamilton, ~workcell, ~flexmap, ~operator,
  "ach", "3", "1", "1", "C", 
  "fch", "3", "1", "1", "C", 
  "fce", "3", "1", "1", "C", 
  "fce", "2", "2", "3", "A", 
  "fce", "2", "2", "3", "B", 
  "fce", "2", "2", "3", "C", 
  "ach", "2", "2", "4", "C", 
  "ach", "2", "1", "4", "C",
  "fce", "1", "2", "5", "B", 
  "fce", "2", "2", "5", "B", 
  "fce", "3", "2", "5", "B",
  "fch", "1", "1", "1", "A",
  "fch", "1", "1", "2", "A",
  "fch", "1", "1", "3", "A",
  "fch", "1", "1", "4", "A",
  "fch", "1", "1", "5", "A",
  "fch", "1", "1", "6", "A",
  "ach", "1", "2", "2", "A", 
  "ach", "1", "1", "3", "B", 
  "ach", "3", "2", "5", "C",
  "ach", "2", "1", "6", "A",
  "ach", "3", "2", "2", "B",
  "ach", "1", "2", "6", "C", 
  "ach", "3", "2", "2", "A", 
  "fch", "3", "2", "4", "B", 
  "fch", "2", "2", "6", "C", 
  "fch", "2", "2", "1", "B", 
  "fce", "2", "1", "2", "B", 
  "fce", "3", "1", "4", "C", 
  "fce", "3", "1", "6", "B"

)
```



```{r}
full_factorial_6_flex <- tidyr::crossing(operator = c("A", "B", "C"), 
                                  hamilton = c("H1", "H2", "H3"), 
                                  lot = c("ach", "fch", "fce"), 
                flexmap = c("F1", "F2", "F3", "F4", "F5", "F6"), 
                workcell = c("1", "2")) 
full_factorial_6_flex %>% 
  ggplot(aes(operator, workcell)) + 
  geom_point() + 
  facet_grid(rows = vars(hamilton, lot), cols = vars(flexmap)) 

current_des %>% 
  ggplot(aes(operator, workcell)) + 
  geom_point() + 
  facet_grid(rows = vars(hamilton, lot), cols = vars(flexmap)) 
```




How does an optimal design look with 6 flexmaps? 

```{r}
panel_1 <- tibble::tribble(
                              ~lot,  ~hamilton,  ~flexmap, ~operator, ~workcell,
                            "ach", "H2", "F4", "C",  "2",
                            "fch", "H2", "F3", "B",  "1",
                            "fce", "H3", "F4", "A",  "1",
                            "fch", "H1", "F5", "C",  "2",
                            "ach", "H1", "F1", "A",  "1",
                            "fce", "H2", "F6", "C",  "1",
                            "fce", "H2", "F1", "B",  "2",
                            "fce", "H1", "F2", "C",  "1",
                            "ach", "H2", "F5", "A",  "1",
                            "fch", "H2", "F2", "A",  "1",
                            "fch", "H3", "F6", "A",  "2",
                            "fce", "H1", "F3", "A",  "2",
                            "fce", "H3", "F5", "B",  "1",
                            "ach", "H3", "F2", "B",  "2",
                            "fch", "H1", "F4", "B",  "1",
                            "ach", "H1", "F6", "B",  "1",
                            "fch", "H3", "F1", "C",  "1",
                            "ach", "H3", "F3", "C",  "1"
                            )
panel_1 %>% 
  ggplot(aes(operator, workcell)) + 
  geom_point() + 
  facet_grid(rows = vars(hamilton, lot), cols = vars(flexmap)) 
```





## Compare the 6Flex with current 6 flex?   

### FF 6 Flex
```{r}
sd_operator = 15
sd_hamilton = 10
sd_lot = 15
sd_flex = 10
sd_wc = 5
sd_error = 5
beta_0 = 400

get_estimates_ff_6f <- function(sd_operator = 15,
                             sd_hamilton = 10,
                             sd_lot = 15,
                             sd_flex = 10,
                             sd_wc = 10,
                             sd_error = 5,
                             beta_0 = 400) {
  operator <- data.frame(operator = c("A", "B", "C"),
                         operator_i = rnorm(3, 0, sd_operator))
  hamilton <- data.frame(hamilton = c("H1", "H2", "H3"),
                         ham_i = rnorm(3, 0, sd_hamilton))
  lot <- data.frame(lot = c("l1", "l2", "l3"),
                    lot_i = rnorm(3, 0, sd_lot))
  flexmap <- data.frame(flexmap = c("F1", "F2", "F3", "F4", "F5", "F6"),
                        flex_i = rnorm(3, 0, sd_flex))
  workcell <- data.frame(workcell = c("1", "2"),
                         wc_i = rnorm(2, 0, sd_wc))
  
  sim_data <-
    tidyr::crossing(operator, hamilton, lot, flexmap, workcell) %>%
    mutate(e_i = rnorm(nrow(.), 0, sd_error)) %>%
    mutate(response = beta_0 + operator_i + ham_i + lot_i + flex_i + wc_i + e_i) %>%
    select(operator, hamilton, lot, flexmap, workcell, response)
  
  sim_mod <- lme4::lmer(response ~ (1 | operator) + (1 | hamilton) + (1 | lot) +
                          (1 | flexmap) + (1 | workcell),
                        data = sim_data)
  sd_estimates <- VarCorr(sim_mod) %>%
    data.frame() %>%
    select(grp, sdcor)
  
  return_df <- ranef(sim_mod) %>% 
  data.frame() %>% 
  group_by(grpvar) %>% 
  summarise(avg = mean(condval)) %>% 
  rename(grp = grpvar) %>% 
  inner_join(sd_estimates) %>% 
  mutate(grand_mean = fixef(sim_mod)) %>% 
  mutate(perc_cv = 100*(sdcor/(grand_mean))) %>% 
  mutate(true_cv = case_when(grp == "flexmap" ~ 100*sd_flex/beta_0, 
                             grp == "hamilton" ~ 100*sd_hamilton/beta_0, 
                             grp == "lot" ~ 100*sd_lot/beta_0, 
                             grp == "operator" ~ 100*sd_operator/beta_0, 
                             grp == "workcell" ~ 100*sd_wc/beta_0), 
         true_sd = case_when(grp == "flexmap" ~ sd_flex, 
                             grp == "hamilton" ~ sd_hamilton, 
                             grp == "lot" ~ sd_lot, 
                             grp == "operator" ~ sd_operator, 
                             grp == "workcell" ~ sd_wc))
  
    return(return_df)
  
}
```

```{r}
sim_factorial_6flex <- purrr::imap_dfr(1:1000, ~ get_estimates_ff_6f())

sim_factorial_6flex %>% 
  ggplot(.,aes(grp, sdcor)) + 
  geom_boxplot() + 
  geom_point(aes(x = grp, y = true_sd), color = "red") 

sim_factorial_6flex %>% 
  filter(perc_cv == 0) %>% 
  nrow(.)/nrow(sim_factorial_6flex)
```

### Manual 6 FLEX 
How does are manual design do? 

```{r}
manual_6_flex  <- function(sd_operator = 15,
                             sd_hamilton = 10,
                             sd_lot = 15,
                             sd_flex = 10,
                             sd_wc = 5,
                             sd_error = 5,
                             beta_0 = 400) {
  operator <- data.frame(operator = c("A", "B", "C"),
                         operator_i = rnorm(3, 0, sd_operator))
  hamilton <- data.frame(hamilton = c("1", "2", "3"),
                         ham_i = rnorm(3, 0, sd_hamilton))
  lot <- data.frame(lot = c("ach", "fch", "fce"),
                    lot_i = rnorm(3, 0, sd_lot))
  flexmap <- data.frame(flexmap = c("1", "2", "3", "4", "5", "6"),
                        flex_i = rnorm(3, 0, sd_flex))
  workcell <- data.frame(workcell = c("1", "2"),
                         wc_i = rnorm(2, 0, sd_wc))
  
  sim_data <-
    tidyr::crossing(operator, hamilton, lot, flexmap, workcell) %>%
    mutate(e_i = rnorm(nrow(.), 0, sd_error)) %>%
    mutate(response = beta_0 + operator_i + ham_i + lot_i + flex_i + wc_i + e_i) %>%
    select(operator, hamilton, lot, flexmap, workcell, response)
  
  
  
  
  sim_mod <- current_des %>% 
    inner_join(sim_data, by = c("lot", "hamilton", "flexmap", "operator", "workcell")) %>% 
    lme4::lmer(response ~ (1 | operator) + (1 | hamilton) + (1 | lot) +
                          (1 | flexmap) + (1 | workcell),
                        data = .)
  sd_estimates <- VarCorr(sim_mod) %>%
    data.frame() %>%
    select(grp, sdcor)
  
  return_df <- ranef(sim_mod) %>% 
  data.frame() %>% 
  group_by(grpvar) %>% 
  summarise(avg = mean(condval)) %>% 
  rename(grp = grpvar) %>% 
  inner_join(sd_estimates) %>% 
  mutate(grand_mean = fixef(sim_mod)) %>% 
  mutate(perc_cv = 100*(sdcor/(grand_mean))) %>% 
  mutate(true_cv = case_when(grp == "flexmap" ~ 100*sd_flex/beta_0, 
                             grp == "hamilton" ~ 100*sd_hamilton/beta_0, 
                             grp == "lot" ~ 100*sd_lot/beta_0, 
                             grp == "operator" ~ 100*sd_operator/beta_0, 
                             grp == "workcell" ~ 100*sd_wc/beta_0), 
         true_sd = case_when(grp == "flexmap" ~ sd_flex, 
                             grp == "hamilton" ~ sd_hamilton, 
                             grp == "lot" ~ sd_lot, 
                             grp == "operator" ~ sd_operator, 
                             grp == "workcell" ~ sd_wc))
  
    return(return_df)
  
}
```

```{r}
sim_manual_6flex <- purrr::imap_dfr(1:1000, ~ manual_6_flex())

sim_manual_6flex %>% 
  ggplot(.,aes(grp, sdcor)) + 
  geom_boxplot() + 
  geom_point(aes(x = grp, y = true_sd), color = "red") 

sim_manual_6flex %>% 
  filter(perc_cv == 0) %>% 
  nrow(.)/nrow(sim_manual_6flex)
```


```{r}
sim_factorial_6flex %>% 
  mutate(design = rep("factorial", nrow(.))) -> sim_factorial_6flex
sim_manual_6flex %>% 
  mutate(design = rep("manual", nrow(.))) -> sim_manual_6flex

bind_rows(sim_factorial_6flex, sim_manual_6flex) %>% 
  ggplot(.,aes(design, sdcor)) + 
  geom_boxplot() + 
  facet_grid(cols = vars(grp)) + 
  labs(title = "Distribution of SD estimates")
```


Compare failures  

```{r}
factorial_6_fail <- sim_factorial_6flex %>% 
  group_by(grp) %>% 
  filter(perc_cv == 0) %>% 
  count(grp) %>% 
  ungroup() %>% 
  mutate(design = rep("factorial", nrow(.)))

manual_6_fail <- sim_manual_6flex %>% 
  group_by(grp) %>% 
  filter(perc_cv == 0) %>% 
  count(grp) %>% 
  ungroup() %>% 
  mutate(design = rep("manual", nrow(.)))

bind_rows(factorial_6_fail, manual_6_fail) %>% 
  mutate(prop = 100*(n/1000)) %>% 
  ggplot(., aes(design, prop)) + 
  geom_point() + 
  facet_grid(cols = vars(grp)) + 
  labs(title = "% of time variance was estimated to be zero") + 
  scale_y_continuous(breaks = seq(0, 18, by = 2))

```










A nuance while comparing the 3 methods is that the optimal and full factorial are assuming only 3 flexmaps   

```{r}
current_des <- current_des %>% 
  mutate(flexmap = case_when(flexmap == "4" ~ "1", 
                   flexmap == "5" ~ "2", 
                   flexmap == "6" ~ "3", 
                   TRUE ~ as.character(flexmap)))
  
```







## Simulation   

Simulate data with fixed standard deviations for each source of variation   

We have five factors  - 

1. operator - 3 levels O1, O2 and O3   
2. Hamilton - H1, H2, H3  
3. Lot - L1, L2, L3  
4. Flexmap  - F1, F2, F3 
5. Workcell - W1, W2   




Write a function that  
1. Simulates data  
2. Fits model 
3. Extracts variance estimates 
4. Extracts intercept 
5. Calculates estimated % CV 

We will then iterate over 1000 times and create a data frame. 

**1**  
```{r}
sd_operator = 15
sd_hamilton = 10
sd_lot = 15
sd_flex = 10
sd_wc = 5
sd_error = 5
beta_0 = 400
```

**Factorial function**   
```{r}
get_estimates_ff <- function(sd_operator = 15,
                             sd_hamilton = 10,
                             sd_lot = 15,
                             sd_flex = 10,
                             sd_wc = 5,
                             sd_error = 5,
                             beta_0 = 400) {
  operator <- data.frame(operator = c("o1", "o2", "03"),
                         operator_i = rnorm(3, 0, sd_operator))
  hamilton <- data.frame(hamilton = c("h1", "h2", "h3"),
                         ham_i = rnorm(3, 0, sd_hamilton))
  lot <- data.frame(lot = c("l1", "l2", "l3"),
                    lot_i = rnorm(3, 0, sd_lot))
  flexmap <- data.frame(flexmap = c("f1", "f2", "f3"),
                        flex_i = rnorm(3, 0, sd_flex))
  workcell <- data.frame(workcell = c("w1", "w2"),
                         wc_i = rnorm(2, 0, sd_wc))
  
  sim_data <-
    tidyr::crossing(operator, hamilton, lot, flexmap, workcell) %>%
    mutate(e_i = rnorm(nrow(.), 0, sd_error)) %>%
    mutate(response = beta_0 + operator_i + ham_i + lot_i + flex_i + wc_i + e_i) %>%
    select(operator, hamilton, lot, flexmap, workcell, response)
  
  sim_mod <- lme4::lmer(response ~ (1 | operator) + (1 | hamilton) + (1 | lot) +
                          (1 | flexmap) + (1 | workcell),
                        data = sim_data)
  sd_estimates <- VarCorr(sim_mod) %>%
    data.frame() %>%
    select(grp, sdcor)
  
  return_df <- ranef(sim_mod) %>% 
  data.frame() %>% 
  group_by(grpvar) %>% 
  summarise(avg = mean(condval)) %>% 
  rename(grp = grpvar) %>% 
  inner_join(sd_estimates) %>% 
  mutate(grand_mean = fixef(sim_mod)) %>% 
  mutate(perc_cv = 100*(sdcor/(avg + grand_mean))) %>% 
  mutate(true_cv = case_when(grp == "flexmap" ~ 100*sd_flex/beta_0, 
                             grp == "hamilton" ~ 100*sd_hamilton/beta_0, 
                             grp == "lot" ~ 100*sd_lot/beta_0, 
                             grp == "operator" ~ 100*sd_operator/beta_0, 
                             grp == "workcell" ~ 100*sd_wc/beta_0), 
         true_sd = case_when(grp == "flexmap" ~ sd_flex, 
                             grp == "hamilton" ~ sd_hamilton, 
                             grp == "lot" ~ sd_lot, 
                             grp == "operator" ~ sd_operator, 
                             grp == "workcell" ~ sd_wc))
  
    return(return_df)
  
}
```


```{r}
sim_factorial <- purrr::imap_dfr(1:1000, ~ get_estimates_ff())

sim_factorial %>% 
  ggplot(.,aes(grp, perc_cv)) + 
  geom_boxplot() + 
  geom_point(aes(x = grp, y = true_cv), color = "red") 

factorial_80_interval <- sim_factorial %>% 
  group_by(grp) %>% 
  summarise(mean_sd = mean(sdcor), lower = quantile(sdcor, 0.10), 
            upper = quantile(sdcor, 0.9), 
            mean_cv = mean(perc_cv), 
            lower_cv = quantile(perc_cv, 0.1), 
            upper_cv = quantile(perc_cv, 0.9)) %>% 
  mutate(true_sd = case_when(grp == "flex" ~ sd_flex, 
                             grp == "ham" ~ sd_hamilton, 
                             grp == "l" ~ sd_lot, 
                             grp == "op" ~ sd_operator, 
                             grp == "wc" ~ sd_wc)) %>% 
  mutate(grp = case_when(grp == "flex" ~ "flexmap", 
                         grp == "ham" ~ "hamilton", 
                         grp == "l" ~ "lot",
                         grp == "op" ~ "operator", 
                         grp == "wc" ~ "workcell"), 
         design = rep("factorial", 5)) %>% 
  mutate(true_cv = case_when(grp == "flexmap" ~ 100*sd_flex/beta_0, 
                             grp == "hamilton" ~ 100*sd_hamilton/beta_0, 
                             grp == "lot" ~ 100*sd_lot/beta_0, 
                             grp == "operator" ~ 100*sd_operator/beta_0, 
                             grp == "workcell" ~ 100*sd_wc/beta_0))
```

#### Current Design   

Jackie design should technically be a subset of the full design  - but seems like it isn't. There are some runs that aren't even part of a full factorial experiment???? 

```{r}
current_des %>% 
  ggplot(.,aes(workcell, flexmap)) + 
  geom_point() + 
  facet_grid(rows = vars(lot), cols = vars(operator, hamilton)) + 
  theme_classic() 

optimal %>% 
  ggplot(.,aes(workcell, flexmap)) + 
  geom_point() + 
  facet_grid(rows = vars(lot), cols = vars(operator, hamilton)) + 
  theme_classic() 
```



```{r}
jackie_sim_estimate <- function(sd_operator = 15,
                             sd_hamilton = 10,
                             sd_lot = 15,
                             sd_flex = 10,
                             sd_wc = 5,
                             sd_error = 5,
                             beta_0 = 400) {
  operator <- data.frame(operator = c("A", "B", "C"),
                         operator_i = rnorm(3, 0, sd_operator))
  hamilton <- data.frame(hamilton = c("1", "2", "3"),
                         ham_i = rnorm(3, 0, sd_hamilton))
  lot <- data.frame(lot = c("ace", "ach", "fce"),
                    lot_i = rnorm(3, 0, sd_lot))
  flexmap <- data.frame(flexmap = c("1", "2", "3"),
                        flex_i = rnorm(3, 0, sd_flex))
  workcell <- data.frame(workcell = c("1", "2"),
                         wc_i = rnorm(2, 0, sd_wc))

sim_data <- tidyr::crossing(operator, hamilton, lot, flexmap, workcell) %>% 
  mutate(e_i = rnorm(nrow(.), 0, sd_error)) %>% 
  mutate(response = beta_0 + operator_i + ham_i + lot_i + flex_i + wc_i + e_i) %>% 
  select(operator, hamilton, lot, flexmap, workcell, response)

 sim_mod <- current_des %>% 
  inner_join(sim_data, by = c("lot", "hamilton", "flexmap", "operator", "workcell")) %>% 
  lme4::lmer(response ~ (1 | operator) + (1 | hamilton) + (1 | lot) +
                          (1 | flexmap) + (1 | workcell),
                        data = .)
 
  sd_estimates <- VarCorr(sim_mod) %>%
    data.frame() %>%
    select(grp, sdcor)
  
  return_df <- ranef(sim_mod) %>% 
  data.frame() %>% 
  group_by(grpvar) %>% 
  summarise(avg = mean(condval)) %>% 
  rename(grp = grpvar) %>% 
  inner_join(sd_estimates) %>% 
  mutate(grand_mean = fixef(sim_mod)) %>% 
  mutate(perc_cv = 100*(sdcor/(avg + grand_mean))) %>% 
  mutate(true_cv = case_when(grp == "flexmap" ~ 100*sd_flex/beta_0, 
                             grp == "hamilton" ~ 100*sd_hamilton/beta_0, 
                             grp == "lot" ~ 100*sd_lot/beta_0, 
                             grp == "operator" ~ 100*sd_operator/beta_0, 
                             grp == "workcell" ~ 100*sd_wc/beta_0))
  
    return(return_df)
  

}
```


```{r}
sim_jackie <- purrr::imap_dfr(1:1000, ~ jackie_sim_estimate())

sim_jackie %>% 
  ggplot(.,aes(grp, perc_cv)) + 
  geom_boxplot() + 
  geom_point(aes(x = grp, y = true_cv), color = "red")

sim_jackie %>% 
  filter(perc_cv == 0)

jackie_80_interval <- sim_jackie %>% 
  group_by(grp) %>% 
  summarise(mean_sd = mean(sdcor), lower = quantile(sdcor, 0.10), 
            upper = quantile(sdcor, 0.9), 
            mean_cv = mean(perc_cv), 
            lower_cv = quantile(perc_cv, 0.1), 
            upper_cv = quantile(perc_cv, 0.9))%>% 
  mutate(true_sd = case_when(grp == "flexmap" ~ sd_flex, 
                             grp == "hamilton" ~ sd_hamilton, 
                             grp == "lot" ~ sd_lot, 
                             grp == "operator" ~ sd_operator, 
                             grp == "workcell" ~ sd_wc)) %>%
  mutate(true_cv = case_when(grp == "flexmap" ~ 100*sd_flex/beta_0, 
                             grp == "hamilton" ~ 100*sd_hamilton/beta_0, 
                             grp == "lot" ~ 100*sd_lot/beta_0, 
                             grp == "operator" ~ 100*sd_operator/beta_0, 
                             grp == "workcell" ~ 100*sd_wc/beta_0)) %>% 
  mutate(design = rep("current", 5))

```






#### Optimal Design  

```{r}
full_factorial %>% 
  ggplot(.,aes(operator, workcell)) + 
  geom_point() + 
  facet_grid(rows = vars(hamilton, lot), 
             cols = vars(flexmap))

optimal %>% 
  ggplot(.,aes(operator, workcell)) + 
  geom_point() + 
  facet_grid(rows = vars(hamilton, lot), 
             cols = vars(flexmap))

ff <- full_factorial 
op <- optimal %>% 
  mutate(design = rep("optimal", nrow(.)))
ff %>% 
  left_join(op) %>% 
  ggplot(.,aes(operator, workcell)) + 
  geom_point(aes(color = design)) + 
  facet_grid(rows = vars(hamilton, lot), 
             cols = vars(flexmap))

op %>% 
  ggplot(.,aes(operator, workcell)) + 
  geom_point() + 
  facet_grid(rows = vars(hamilton, lot), 
             cols = vars(flexmap))
```


```{r}
optimal_sim_estimate <- function(sd_operator = 15,
                             sd_hamilton = 10,
                             sd_lot = 15,
                             sd_flex = 10,
                             sd_wc = 5,
                             sd_error = 5,
                             beta_0 = 400, 
                             data = optimal) {
  
  operator <- data.frame(operator = c("A", "B", "C"),
                         operator_i = rnorm(3, 0, sd_operator))
  hamilton <- data.frame(hamilton = c("1", "2", "3"),
                         ham_i = rnorm(3, 0, sd_hamilton))
  lot <- data.frame(lot = c("ace", "ach", "fce"),
                    lot_i = rnorm(3, 0, sd_lot))
  flexmap <- data.frame(flexmap = c("1", "2", "3"),
                        flex_i = rnorm(3, 0, sd_flex))
  workcell <- data.frame(workcell = c("1", "2"),
                         wc_i = rnorm(2, 0, sd_wc))

sim_data <- tidyr::crossing(operator, hamilton, lot, flexmap, workcell) %>% 
  mutate(e_i = rnorm(nrow(.), 0, sd_error)) %>% 
  mutate(response = beta_0 + operator_i + ham_i + lot_i + flex_i + wc_i + e_i) %>% 
  select(operator, hamilton, lot, flexmap, workcell, response)

 sim_mod <- data %>% 
  inner_join(sim_data, by = c("lot", "hamilton", "flexmap", "operator", "workcell")) %>% 
  lme4::lmer(response ~ (1 | operator) + (1 | hamilton) + (1 | lot) +
                          (1 | flexmap) + (1 | workcell),
                        data = .)
 
  sd_estimates <- VarCorr(sim_mod) %>%
    data.frame() %>%
    select(grp, sdcor)
  
  return_df <- ranef(sim_mod) %>% 
  data.frame() %>% 
  group_by(grpvar) %>% 
  summarise(avg = mean(condval)) %>% 
  rename(grp = grpvar) %>% 
  inner_join(sd_estimates) %>% 
  mutate(grand_mean = fixef(sim_mod)) %>% 
  mutate(perc_cv = 100*(sdcor/(avg + grand_mean))) %>% 
  mutate(true_cv = case_when(grp == "flexmap" ~ 100*sd_flex/beta_0, 
                             grp == "hamilton" ~ 100*sd_hamilton/beta_0, 
                             grp == "lot" ~ 100*sd_lot/beta_0, 
                             grp == "operator" ~ 100*sd_operator/beta_0, 
                             grp == "workcell" ~ 100*sd_wc/beta_0), 
         true_sd = case_when(grp == "flexmap" ~ sd_flex, 
                             grp == "hamilton" ~ sd_hamilton, 
                             grp == "lot" ~ sd_lot, 
                             grp == "operator" ~ sd_operator, 
                             grp == "workcell" ~ sd_wc))
  
    return(return_df)
}
```

```{r}
sim_optimal <- purrr::imap_dfr(1:1000, ~ optimal_sim_estimate())

sim_optimal %>% 
  ggplot(.,aes(grp, perc_cv)) + 
  geom_boxplot() + 
  geom_point(aes(x = grp, y = true_cv), color = "red")

sim_optimal %>% 
  ggplot(.,aes(grp, sdcor)) + 
  geom_boxplot() + 
  geom_point(aes(x = grp, y = true_cv), color = "red")

sim_optimal %>% 
  filter(perc_cv == 0)

optimal_80_interval <- sim_optimal %>% 
  group_by(grp) %>% 
  summarise(mean_sd = mean(sdcor), lower = quantile(sdcor, 0.10), 
            upper = quantile(sdcor, 0.9), 
            mean_cv = mean(perc_cv), 
            lower_cv = quantile(perc_cv, 0.1), 
            upper_cv = quantile(perc_cv, 0.9)) %>% 
  mutate(true_sd = case_when(grp == "flexmap" ~ sd_flex, 
                             grp == "hamilton" ~ sd_hamilton, 
                             grp == "lot" ~ sd_lot, 
                             grp == "operator" ~ sd_operator, 
                             grp == "workcell" ~ sd_wc)) %>% 
  mutate(true_cv = case_when(grp == "flexmap" ~ 100*sd_flex/beta_0, 
                             grp == "hamilton" ~ 100*sd_hamilton/beta_0, 
                             grp == "lot" ~ 100*sd_lot/beta_0, 
                             grp == "operator" ~ 100*sd_operator/beta_0, 
                             grp == "workcell" ~ 100*sd_wc/beta_0)) %>% 
  
  mutate(design = rep("optimal", 5))

optimal_80_interval 
```


### Compare  

```{r}
bind_rows(factorial_80_interval, jackie_80_interval, optimal_80_interval) %>% 
  ggplot(.,aes(design, mean_cv, group = grp)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = lower_cv, ymax = upper_cv), width = 0.5) + 
  facet_grid(cols = vars(grp)) + 
  geom_point(aes(x = design, y = true_cv), color = "red", 
             position = position_dodge(width = 1)) + 
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "80 % of simulation estimates") 


bind_rows(sim_factorial, sim_optimal, .id = "design") %>% 
  mutate(design = case_when(design == "1" ~ "factorial", 
                            design == "2" ~ "optimal")) %>% 
  ggplot(aes(design, sdcor, group = design)) + 
  geom_boxplot() + 
  geom_point(aes(x = design, y = true_sd), color = "red", 
             position = position_dodge(width = 1)) + 
  facet_grid(cols = vars(grp)) + 
  #theme_classic() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


factorial_fail <- sim_factorial %>% 
  group_by(grp) %>% 
  filter(perc_cv == 0) %>% 
  count(grp) %>% 
  ungroup() %>% 
  mutate(design = rep("factorial", nrow(.)))



optimal_fail <- sim_optimal %>% 
  filter(perc_cv == 0) %>% 
  group_by(grp) %>% 
  filter(perc_cv == 0) %>% 
  count(grp) %>% 
  ungroup() %>% 
  mutate(design = rep("optimal", nrow(.)))

bind_rows(factorial_fail, optimal_fail) %>% 
  mutate(n = 100*(n/1000)) %>% 
  ggplot(.,aes(design, n)) + 
  geom_point(color = "purple") + 
  facet_grid(cols = vars(grp)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "Proportion of time variance was estimated to be 0", 
       y = "% of time CV estimated to be 0") + 
  scale_y_continuous(breaks = seq(0, 16, by = 2))
```







### Zero variances   

```{r}
factorial_fail <- sim_factorial %>% 
  group_by(grp) %>% 
  filter(perc_cv == 0) %>% 
  count(grp) %>% 
  ungroup() %>% 
  mutate(design = rep("factorial", nrow(.)))



optimal_fail <- sim_optimal %>% 
  filter(perc_cv == 0) %>% 
  group_by(grp) %>% 
  filter(perc_cv == 0) %>% 
  count(grp) %>% 
  ungroup() %>% 
  mutate(design = rep("optimal", nrow(.)))


current_fail <- sim_jackie %>% 
  group_by(grp) %>% 
  filter(perc_cv == 0) %>% 
  count(grp) %>% 
  ungroup() %>% 
  mutate(design = rep("current", nrow(.)))

bind_rows(factorial_fail, optimal_fail, current_fail) %>% 
  mutate(n = 100*(n/1000)) %>% 
  ggplot(.,aes(design, n)) + 
  geom_point(color = "purple") + 
  facet_grid(cols = vars(grp)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(title = "Proportion of time variance was estimated to be 0", 
       y = "% of time CV estimated to be 0")
```









### 18 run optimal design   

```{r}
optimal_18 <- tibble::tribble(
                                          ~lot, ~workcell, ~hamilton, ~flexmap, ~operator,
                                          "fce",  1L,  3L,  3L, "B",
                                          "ach",  1L,  3L,  2L, "B",
                                          "ach",  1L,  3L,  1L, "C",
                                          "ach",  1L,  1L,  3L, "A",
                                          "fce",  2L,  1L,  2L, "B",
                                          "fch",  1L,  2L,  2L, "A",
                                          "fch",  2L,  3L,  2L, "A",
                                          "fch",  1L,  1L,  1L, "B",
                                          "fch",  2L,  2L,  1L, "B",
                                          "fce",  2L,  3L,  1L, "A",
                                          "fce",  1L,  2L,  2L, "C",
                                          "ach",  2L,  1L,  2L, "C",
                                          "fce",  1L,  2L,  2L, "C",
                                          "ach",  2L,  2L,  3L, "B",
                                          "ach",  2L,  2L,  1L, "A",
                                          "fch",  2L,  3L,  3L, "C",
                                          "ach",  1L,  1L,  3L, "A",
                                          "fch",  2L,  3L,  3L, "C"
                                          ) %>% 
  mutate(lot = tolower(lot)) %>% 
  mutate_all(., ~ as.character(.x))

```


```{r}
sim_optimal_18 <- purrr::imap_dfr(1:1000, ~ optimal_sim_estimate(data = optimal_18))

sim_optimal_18 %>% 
  ggplot(.,aes(grp, perc_cv)) + 
  geom_boxplot() + 
  geom_point(aes(x = grp, y = true_cv), color = "red")

sim_optimal_18 %>% 
  ggplot(.,aes(grp, sdcor)) + 
  geom_boxplot() + 
  geom_point(aes(x = grp, y = true_cv), color = "red")

sim_optimal_18 %>% 
  filter(perc_cv == 0)

optimal_18_80_interval <- sim_optimal_18 %>% 
  group_by(grp) %>% 
  summarise(mean_Sd = mean(sdcor), lower = quantile(sdcor, 0.10), 
            upper = quantile(sdcor, 0.9)) %>% 
  mutate(true_sd = case_when(grp == "flexmap" ~ sd_flex, 
                             grp == "hamilton" ~ sd_hamilton, 
                             grp == "lot" ~ sd_lot, 
                             grp == "operator" ~ sd_operator, 
                             grp == "workcell" ~ sd_wc)) %>% 
  mutate(design = rep("optimal", 5))

```


```{r}
bind_rows(factorial_80_interval, jackie_80_interval, optimal_80_interval) %>% 
  ggplot(.,aes(design, mean_sd, group = grp)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.5) + 
  facet_grid(cols = vars(grp)) + 
  geom_point(aes(x = design, y = true_sd), color = "red", 
             position = position_dodge(width = 1)) + 
  theme_classic() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```














