---
title: "beta-lot-experiments"
author: "Dilsher Singh Dhillon"
date: "`r format(Sys.time(),'%d %B,%Y')`"
output:
  html_document:
    toc: true
    toc_float : true 
---
<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: #948DFF;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```



<font size="4" color="#1DE3FE">  

## Introduction    

</font>  


```{r}
library(tidyverse)
freenome_colors <- c('#948DFF', '#1DE3FE', '#BBD532', '#FF9D42',  '#FC2E7B', 
                   '#FECDD1')
```

```
pate-rnd xmap-collector --include_file_str 20220119_WC_P1vP6 \
  --include_file_str  20220120_ShakeSpd_1000rpm_Panel1_Plate1 \
  --include_file_str  20220120_ShakeSpd_1200rpm_Panel1_Plate2 \
  --include_file_str  20220120_ShakeSpd_1500rpm_Panel1_Plate3 \
  --include_file_str  20220120_ShakeSpd_1000rpm_Panel2_Plate1 \
  --include_file_str  20220120_ShakeSpd_1200rpm_Panel2_Plate2 \
  --include_file_str  20220120_ShakeSpd_1500rpm_Panel2_Plate3 \
  --include_file_str  20220120_ShakeSpd_1200rpm_Panel2_Plate2 \
  --include_file_str  20220120_ShakeSpd_1500rpm_Panel2_Plate2 \
  --include_file_str  Beta \
  --include_file_str  Interf \
  --include_file_str  PltStd \
  --include_file_str  Endogenous \
  --include_file_str  Exogenous \
  --include_file_str  Platinum \
  --include_file_str  Reproducibility \
  --include_file_str  Donor_Screening \
  --include_file_str  PlatinumStd \
  --include_file_str  HamiltonEquiv\
  --include_file_str  ShakingCompare \
  --include_file_str  20211221_DLS_Matrix_Int \
  --include_sample_str Standard --include_sample_str Buffer --include_sample_str Background --include_sample_str QC --include_sample_str RC  --ignore_case_sample \
  --out_file_name betalot_experiments-2022-01-25.csv
```


```
gsutil cp gs://inhouse-xmap-data/user_data_frames/betalot_experiments-2022-01-25.csv ~/'google drive'/'my drive'/projects/beta-av-testing/data/raw/beta-lot-stds-controls-2022-01-25.csv
```



### Read in data 

```{r}
raw <- read_csv(here::here("data", "raw", "beta-lot-stds-controls-2022-01-25.csv")) # nolint

raw <- raw %>% 
  mutate(batch = str_remove(file_name, "_[0-9]+.csv")) %>% 
  filter(!grepl("20211028_Reproducibilit_Panel2_Plate3", file_name))
```


#### SAPE (Controls vs 4hr)        

According to the (benchling)[https://freenome.benchling.com/freenome/f/lib_rLUfj3iF-06-guardbanding-for-automation/etr_sY3wzurA-bwtm-beta-lot-sa-pe-room-temperature-stability-0-4-hour/edit], 
the plate 2 or `P2` in the `file_name` the SAPE is prepared 4 hours earlier.   


```{r}
sape_data <- raw %>% 
    filter(grepl("SAPE", file_name)) %>% 
    filter(grepl("Beta", file_name)) %>% 
    mutate(condition = ifelse(grepl("P2", file_name), "4hr", "control"))

```


We only need to focus on the top 7 proteins of interest.  

```{r}
sape_data <- sape_data %>% 
    filter(assay %in% c("WFDC2", "TNC", "FLT3L", "CEA", "IL-8", 
    "IL-1 R2", "MUC-16"))
```

```{r}
sape_data %>% 
    colnames()
```

```{r}
sape_data %>% 
    filter(sample_type == "standard") %>% 
    dplyr::group_by(xponent_id, assay, condition) %>% 
    dplyr::mutate(median_mfi = mean(median_mfi)) %>% 
    ggplot(., aes(standard_expected_concentration, median_mfi, 
    group = condition)) + 
    geom_point(aes(color = condition), size = 1) + 
    scale_x_log10() + 
    scale_y_log10() + 
    facet_wrap(vars(assay))
```



Is this within our expected range?  We can import the tolerance intervals we generate for beta lot to assess this 

```{r}
mfi_intervals <- read_csv(here::here("data", "processed", 
"beta_lot_spec_limits", 
"provisional_spec_limits-MFI.csv"))
```

```{r}
mfi_intervals <- mfi_intervals %>% 
    filter(assay %in% c("WFDC2", "TNC", "FLT3L", "CEA", "IL-8", 
    "IL-1 R2", "MUC-16")) %>% 
    rename(xponent_id = standard)
```


```{r}
#options(vsc.dev.args = list(width = 10, height = 8, units = "in", res = 300))
```




```{r}
mfi_sape_plots <- function(df = NULL, protein = NULL) {
    df %>% 
    filter(sample_type == "standard") %>% 
    filter(assay == protein) %>%
    dplyr::group_by(xponent_id, assay, condition) %>% 
    dplyr::mutate(median_mfi = mean(median_mfi)) %>% 
    left_join(., mfi_intervals, by = c("assay", "xponent_id")) %>% 
    ggplot(., aes(standard_expected_concentration, median_mfi)) + 
    geom_point(aes(color = condition), size = 1.5, alpha = 1) + 
    geom_errorbar(aes(ymin = lower_limit, ymax = upper_limit), alpha = 0.05, 
    width = 0.15) + 
    scale_x_log10() + 
    scale_y_log10() + 
    theme_classic() + 
    labs(title = paste0(protein), 
         subtitle = "Error Bars are provisional spec limits")
}
```

```{r}
purrr::map(c("CEA", "IL-8", "WFDC2", "FLT3L", "IL-1 R2", "IL-8", "TNC"), ~ mfi_sape_plots(df = sape_data, protein = .x))
```



Compare run controls?   

These experiments don't have run controls on them?   

```{r}
raw %>%
  filter(grepl("SAPE", file_name)) %>% 
    filter(grepl("Beta", file_name)) %>% 
    mutate(condition = ifelse(grepl("P2", file_name), "4hr", "control")) %>% 
   filter(assay %in% c("WFDC2", "TNC", "FLT3L", "CEA", "IL-8", 
    "IL-1 R2", "MUC-16")) %>% 
  count(sample_type)
```
**Extract all standard 5 MFIs for CEA using the tolerance data**    

```{r}
reference_data <- raw %>% 
  mutate(batch = str_remove(file_name, "_[0-9]+.csv")) %>% 
  #filter(lot_number == "1641339" | lot_number == "1641338") %>% 
  filter(!grepl("20211028_Reproducibilit_Panel2_Plate3", file_name)) %>% 
  filter(!grepl("SAPE", file_name)) %>% 
  filter(sample_type == "standard") %>% 
  filter(assay == "CEA") 

current_data <- sape_data %>% 
  filter(assay == "CEA") %>% 
  filter(xponent_id == "Standard5") %>% 
  group_by(condition) %>% 
  summarise(avg_mfi = mean(median_mfi))


### check how many times we see mfis of > 425 ? 
reference_data %>% 
  filter(xponent_id == "Standard5") %>% 
  group_by(file_name) %>% 
  summarise(median_mfi = mean(median_mfi)) %>% 
  filter(median_mfi > 200) %>% 
  mutate(greater = ifelse(median_mfi >=425, 1, 0)) %>% 
  count(greater)


reference_data %>% 
  filter(xponent_id == "Standard5") %>% 
  group_by(file_name) %>% 
  summarise(median_mfi = mean(median_mfi)) %>% 
  filter(median_mfi > 200) %>% 
  ggplot(.,aes(median_mfi)) + 
  #geom_histogram(bins = 30) + 
  geom_density() + 
  #scale_x_log10() + 
  geom_vline(data = current_data, mapping = aes(xintercept = avg_mfi, color = condition)) + 
  theme_classic() + 
  labs(title = "Distribution of Standard 5 using historical runs")
```

**Recovery**  

Does this translate to recovery?  

```{r}
recovery_intervals <- read_csv(here::here("data", "processed", 
"beta_lot_spec_limits", 
"provisional_spec_limits-pct-recovery.csv")) %>% 
  rename(xponent_id = standard)
```

```{r}
current_data <- sape_data %>% 
  filter(assay == "CEA") %>% 
  filter(xponent_id == "Standard5") %>% 
  group_by(condition) %>% 
  summarise(avg_recovery = mean(pct_recovery))


reference_data %>% 
  filter(xponent_id == "Standard5") %>% 
  group_by(file_name) %>% 
  summarise(avg_recovery = mean(pct_recovery)) %>% 
  mutate(greater = ifelse(avg_recovery > 106.64, 1, 0)) %>% 
  count(greater)


reference_data %>% 
  filter(xponent_id == "Standard5") %>% 
  filter(pct_recovery < 200) %>% 
  ggplot(.,aes(pct_recovery)) + 
  geom_density() + 
  #geom_histogram(bins = 30) + 
  geom_vline(data = current_data, mapping = aes(xintercept = avg_recovery, color = condition)) + 
  theme_classic() + 
  labs(title = "Distirbution of % recovery for standard 5")
```



**recovery plots**    








#### Workcell experiments    

```
## get data from GCS  
pate-rnd xmap-collector --include_file_str 20220119_WC_P1vP6 \
  --include_file_str  20220119_WC_P1vP6 \
  --include_sample_str Standard --include_sample_str Buffer --include_sample_str Background --include_sample_str QC --ignore_case_sample \
  --out_file_name workcell-experiments-january-01-26.csv
```

```
gsutil cp gs://inhouse-xmap-data/user_data_frames/workcell-experiments-january-01-26.csv ~/'google drive'/'my drive'/projects/beta-av-testing/data/raw/workcell-experiments-january-01-26.csv
```


```{r}
wc_data <- readr::read_csv(here::here("data", "raw", "workcell-experiments-january-01-26.csv")) %>% 
  mutate(condition = ifelse(grepl("plate1", file_name), "position-1", "position-6")) 
```
In this case, the SAPE time between plate 1 and plate 6 was 30 minutes. But the SAPE time for plate 1 was also 2 hours (instead of 0 as with the controlled experiment above)   


Let's just compare the same assay CEA and the standard 5 and standard 6  

```{r}
mfi_wc_plots <- function(df = NULL, protein = NULL) {
    df %>% 
    filter(sample_type == "standard") %>% 
    filter(assay == protein) %>%
    dplyr::group_by(xponent_id, assay, condition) %>% 
    dplyr::mutate(median_mfi = mean(median_mfi)) %>% 
    left_join(., mfi_intervals, by = c("assay", "xponent_id")) %>% 
    ggplot(., aes(standard_expected_concentration, median_mfi)) + 
    geom_point(aes(color = condition), size = 1.5, alpha = 1) + 
    geom_errorbar(aes(ymin = lower_limit, ymax = upper_limit), alpha = 0.05, 
    width = 0.15) + 
    scale_x_log10() + 
    scale_y_log10() + 
    theme_classic() + 
    labs(title = paste0(protein), 
         subtitle = "Error Bars are provisional spec limits")
}
```

```{r}
purrr::map(c("CEA", "MUC-16", "WFDC2", "FLT3L", "IL-1 R2", "IL-8", "TNC"), 
           ~ mfi_wc_plots(df = wc_data, protein = .x))
```

What about % recovery - is that out of spec as well?   

```{r}
recovery_wc_plots <- function(df = NULL, protein = NULL) {
    df %>% 
    filter(sample_type == "standard") %>% 
    filter(assay == protein) %>%
    dplyr::group_by(xponent_id, assay, condition) %>% 
    dplyr::mutate(pct_recovery = mean(pct_recovery)) %>% 
    left_join(., recovery_intervals, by = c("assay", "xponent_id")) %>% 
    ggplot(., aes(xponent_id, pct_recovery)) + 
    geom_point(aes(color = condition), size = 1.5, alpha = 1) + 
    geom_errorbar(aes(ymin = lower_limit, ymax = upper_limit), alpha = 0.05, 
    width = 0.15) + 
    theme_classic() + 
    labs(title = paste0(protein), 
         subtitle = "Error Bars are provisional spec limits")
}
wc_data %>% 
  filter(assay == "MUC-16") %>% 
  filter(sample_type == "standard") %>% 
  count(condition)
```

```{r}
purrr::map(c("CEA", "MUC-16", "WFDC2", "FLT3L", "IL-1 R2", "IL-8", "TNC"), 
           ~ recovery_wc_plots(df = wc_data, protein = .x))
```


why does MUC-16 have more position 6?  

```{r}
wc_data %>% 
  filter(assay == "MUC-16") %>% 
  filter(sample_type == "standard") %>% 
  filter(condition == "position-6")
```








### Hamiltons    

Compare the 3 hamiltons   


```{r}
hamilton_data <- raw %>% 
  filter(grepl("HamiltonEquiv", file_name)) %>% 
  filter(assay %in% c("WFDC2", "TNC", "FLT3L", "CEA", "IL-8", 
    "IL-1 R2", "MUC-16")) %>% 
  mutate(hamilton = case_when(grepl("Plate1", file_name) ~ "H1", 
                              grepl("Plate2", file_name) ~ "H2", 
                              grepl("Plate3", file_name) ~ "H3")) 
```

```{r}
mfi_hamilton_plots <- function(df = NULL, protein = NULL) {
    df %>% 
    filter(sample_type == "standard") %>% 
    filter(assay == protein) %>%
    dplyr::group_by(xponent_id, assay, hamilton) %>% 
    dplyr::mutate(median_mfi = mean(median_mfi)) %>% 
    left_join(., mfi_intervals, by = c("assay", "xponent_id")) %>% 
    ggplot(., aes(standard_expected_concentration, median_mfi)) + 
    geom_point(aes(color = hamilton), size = 1.5, alpha = 1) + 
    geom_errorbar(aes(ymin = lower_limit, ymax = upper_limit), alpha = 0.05, 
    width = 0.15) + 
    scale_x_log10() + 
    scale_y_log10() + 
    theme_classic() + 
    labs(title = paste0(protein), 
         subtitle = "Error Bars are provisional spec limits")
}
```

```{r}
purrr::map(c("CEA", "MUC-16", "WFDC2", "FLT3L", "IL-1 R2", "IL-8", "TNC"), ~ 
             mfi_hamilton_plots(df = hamilton_data, protein = .x))
```

```{r}
hamilton_data %>% 
    filter(xponent_id == "Standard3" | xponent_id == "Standard4") %>% 
    filter(assay == "CEA") %>%
    dplyr::group_by(xponent_id, assay, hamilton) %>% 
    dplyr::mutate(median_mfi = mean(median_mfi)) %>% 
    left_join(., mfi_intervals, by = c("assay", "xponent_id")) %>% 
    ggplot(., aes(standard_expected_concentration, median_mfi)) + 
    geom_point(aes(color = hamilton), size = 1.5, alpha = 1) + 
    geom_errorbar(aes(ymin = lower_limit, ymax = upper_limit), alpha = 0.05, 
                  width = 0.025) +   
    scale_x_log10() + 
    #scale_y_log10() + 
    theme_classic() + 
    labs(title = "CEA Standard 3 and Standard 4", 
         subtitle = "Error Bars are provisional spec limits") 

hamilton_data %>% 
    filter(xponent_id == "Standard1" | xponent_id == "Standard2") %>% 
    filter(assay == "WFDC2") %>%
    dplyr::group_by(xponent_id, assay, hamilton) %>% 
    dplyr::mutate(median_mfi = mean(median_mfi)) %>% 
    left_join(., mfi_intervals, by = c("assay", "xponent_id")) %>% 
    ggplot(., aes(standard_expected_concentration, median_mfi)) + 
    geom_point(aes(color = hamilton), size = 1.5, alpha = 1) + 
    geom_errorbar(aes(ymin = lower_limit, ymax = upper_limit), alpha = 0.05, 
                  width = 0.025) +   
    scale_x_log10() + 
    #scale_y_log10() + 
    theme_classic() + 
    labs(title = "WFDC2 Standard 1 and Standard 2", 
         subtitle = "Error Bars are provisional spec limits") 
```

**Compare with histogram of previous mfis**    

```{r}
current_data <- hamilton_data %>% 
  filter(assay == "CEA") %>% 
  filter(xponent_id == "Standard4" | xponent_id == "Standard3") %>% 
  group_by(hamilton, xponent_id) %>% 
  summarise(median_mfi = mean(median_mfi))

current_data

### check how many times we see mfis of > 425 ? 
reference_data %>% 
  filter(xponent_id == "Standard4") %>% 
  #group_by(file_name) %>% 
  #summarise(avg_mfi = mean(median_mfi)) %>% 
  mutate(greater = ifelse(median_mfi >=1280.750, 1, 0)) %>% 
  count(greater)


reference_data %>% 
  filter(xponent_id == "Standard3") %>% 
  ggplot(.,aes(median_mfi)) + 
  geom_histogram(bins = 30) + 
  geom_vline(data = current_data %>% filter(xponent_id == "Standard3"), 
             mapping = aes(xintercept = median_mfi, color = hamilton)) + 
  theme_classic() + 
  labs(title = "CEA Standard 3")

reference_data %>% 
  filter(xponent_id == "Standard4") %>% 
  ggplot(.,aes(median_mfi)) + 
  geom_histogram(bins = 30) + 
  geom_vline(data = current_data %>% filter(xponent_id == "Standard4"), 
             mapping = aes(xintercept = median_mfi, color = hamilton)) + 
  theme_classic() + 
    labs(title = "CEA Standard 4")

```



```{r}
hamilton_data %>% 
    #filter(xponent_id == "Standard3" | xponent_id == "Standard4") %>% 
    filter(assay == "CEA") %>%
    dplyr::group_by(xponent_id, assay, hamilton) %>% 
    dplyr::mutate(pct_recovery = mean(pct_recovery)) %>% 
    left_join(., recovery_intervals, by = c("assay", "xponent_id")) %>% 
    ggplot(., aes(xponent_id, pct_recovery)) + 
    geom_point(aes(color = hamilton), size = 1.5, alpha = 1) + 
    geom_errorbar(aes(ymin = lower_limit, ymax = upper_limit), alpha = 0.05, 
                  width = 0.025) +   
   #facet_wrap(vars(assay)) + 
    theme_classic() + 
    labs(title = "CEA % Recovery Across 3 Hamiltons", 
         subtitle = "Error Bars are provisional spec limits") 
  
```





















### Shaking compare    


```{r}
shaking_compare <- raw %>% 
  filter(grepl("20211214", file_name, ignore.case = TRUE)) %>% 
  mutate(condition = ifelse(grepl("Auto", file_name), "Auto", "Not-Auto")) %>%
  filter(assay %in% c("WFDC2", "TNC", "FLT3L", "CEA", "IL-8", 
    "IL-1 R2", "MUC-16"))
shaking_compare %>% 
  count(assay) 

```

```{r}
mfi_shaking_plots <- function(df = NULL, protein = NULL) {
    df %>% 
    filter(sample_type == "standard") %>% 
    filter(assay == protein) %>%
    dplyr::group_by(xponent_id, assay, condition) %>% 
    dplyr::mutate(median_mfi = mean(median_mfi, na.rm = TRUE)) %>% 
    left_join(., mfi_intervals, by = c("assay", "xponent_id")) %>% 
    ggplot(., aes(standard_expected_concentration, median_mfi)) + 
    geom_point(aes(color = condition), size = 1.5, alpha = 1) + 
    geom_errorbar(aes(ymin = lower_limit, ymax = upper_limit), alpha = 0.05, 
    width = 0.15) + 
    scale_x_log10() + 
    scale_y_log10() + 
    theme_classic() + 
    labs(title = paste0(protein), 
         subtitle = "Error Bars are provisional spec limits")
}
```

```{r}
purrr::map(c("CEA", "IL-8", "WFDC2", "FLT3L", "IL-1 R2", "IL-8", "TNC"), ~ 
             mfi_shaking_plots(df = shaking_compare, protein = .x))
```



WFDC2 standard 6?    


```{r}
reference_data <- raw %>% 
  filter(!grepl("20211028_Reproducibilit_Panel2_Plate3", file_name)) %>% 
  filter(!grepl("20211214", file_name)) %>% 
  filter(sample_type == "standard") %>% 
  filter(assay == "WFDC2") 

current_data <- shaking_compare %>% 
  filter(assay == "WFDC2") %>% 
  filter(xponent_id == "Standard1") %>% 
  group_by(condition) %>% 
  summarise(avg_mfi = mean(median_mfi))


### check how many times we see mfis of > 425 ? 
reference_data %>% 
  filter(xponent_id == "Standard1") %>% 
  group_by(file_name) %>% 
  summarise(median_mfi = mean(median_mfi)) %>% 
  mutate(greater = ifelse(median_mfi < 61292.35, 1, 0)) %>% 
  count(greater)


reference_data %>% 
  filter(xponent_id == "Standard1") %>% 
  group_by(file_name) %>% 
  summarise(median_mfi = mean(median_mfi)) %>% 
  filter(median_mfi > 200) %>% 
  ggplot(.,aes(median_mfi)) + 
  #geom_histogram(bins = 30) + 
  geom_density() + 
  #scale_x_log10() + 
  geom_vline(data = current_data, mapping = aes(xintercept = avg_mfi, color = condition)) + 
  theme_classic() + 
  labs(title = "WFDC2 Distribution of Standard 1 using historical runs", 
       subtitle = "Distribution includes future experiments conducted")


## does it affect recovery? 
current_data <- shaking_compare %>% 
  filter(assay == "WFDC2") %>% 
  filter(xponent_id == "Standard1") %>% 
  group_by(condition) %>% 
  summarise(pct_recovery = mean(pct_recovery))

reference_data %>% 
  filter(xponent_id == "Standard1") %>% 
  group_by(file_name) %>% 
  summarise(pct_recovery = mean(pct_recovery)) %>% 
  ggplot(.,aes(pct_recovery)) + 
  #geom_histogram(bins = 30) + 
  geom_density() + 
  #scale_x_log10() + 
  geom_vline(data = current_data, mapping = aes(xintercept = pct_recovery, color = condition)) + 
  theme_classic() + 
  labs(title = "WFDC2 Distribution of Standard 1 % Recovery using historical runs", 
       subtitle = "Distribution includes future experiments conducted")

```


### Historical CVs for MFIs   



```{r eval=FALSE, include=FALSE}
raw %>% 
  filter(!grepl("RC", xponent_id)) %>% 
  filter(xponent_id != "Assay Buffer") %>% 
  group_by(batch , assay, xponent_id) %>% 
  summarise(median_mfi = mean(median_mfi), 
            calc_conc = mean(calc_conc, na.rm = TRUE)) %>% 
  ungroup() %>% 
  group_by(assay, xponent_id) %>% 
  summarise(mfi = mean(median_mfi, na.rm = TRUE), 
            sd_mfi = sd(median_mfi, na.rm = TRUE), 
            cv = 100*sd_mfi/mfi, 
            avg_conc = mean(calc_conc, na.rm = TRUE), 
            conc_pct_cv = 100*sd(calc_conc, na.rm = TRUE)/avg_conc) %>% 
  googlesheets4::write_sheet(., ss = "https://docs.google.com/spreadsheets/d/12vPDfu8dhTwoALf8vMfEtxNFpmUmKb5XUXChgRUodtU/edit#gid=0", 
                             sheet = "MFI-CV")
```






















