---
title: "Distribution of Beta Lot Data By Instrument/Operator"
author: "Dilsher Singh Dhillon"
date: "`r format(Sys.time(),'%d %B,%Y')`"
output:
  html_document:
    toc: true
    toc_float : true
    toc_depth: 4
---
<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: #948DFF;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(plotly)
library(DT)
```

```{r}
options(gargle_oauth_email = TRUE)
```


<font size="4" color="#BBD532">  

## Introduction    

</font>  

**Using data uptill 25th January**   

```
pate-rnd xmap-collector --include_file_str 20220119_WC_P1vP6 \
  --include_file_str  20220120_ShakeSpd_1000rpm_Panel1_Plate1 \
  --include_file_str  20220120_ShakeSpd_1200rpm_Panel1_Plate2 \
  --include_file_str  20220120_ShakeSpd_1500rpm_Panel1_Plate3 \
  --include_file_str  20220120_ShakeSpd_1000rpm_Panel2_Plate1 \
  --include_file_str  20220120_ShakeSpd_1200rpm_Panel2_Plate2 \
  --include_file_str  20220120_ShakeSpd_1500rpm_Panel2_Plate3 \
  --include_file_str  20220120_ShakeSpd_1200rpm_Panel2_Plate2 \
  --include_file_str  20220120_ShakeSpd_1500rpm_Panel2_Plate2 \
  --include_file_str  Beta \
  --include_file_str  Interf \
  --include_file_str  PltStd \
  --include_file_str  Endogenous \
  --include_file_str  Exogenous \
  --include_file_str  Platinum \
  --include_file_str  Reproducibility \
  --include_file_str  Donor_Screening \
  --include_file_str  PlatinumStd \
  --include_file_str  HamiltonEquiv\
  --include_file_str  ShakingCompare \
  --include_file_str  20211221_DLS_Matrix_Int \
  --include_sample_str Standard --include_sample_str Buffer --include_sample_str Background --include_sample_str QC --include_sample_str RC  --ignore_case_sample \
  --out_file_name betalot_experiments-2022-01-25.csv
```


```
gsutil cp gs://inhouse-xmap-data/user_data_frames/betalot_experiments-2022-01-25.csv ~/'google drive'/'my drive'/projects/beta-av-testing/data/raw/beta-lot-stds-controls-2022-01-25.csv
```


This notebook aims to explore the distribution of Flexmaps and Hamiltons using the beta lot data. We will  - 

1. Extract xMAP controls and standards data  
2. Extract the xmap [log](https://docs.google.com/spreadsheets/d/1apRR9pYI0JXyZnKiISMVLC10kFAJ7Bp7KrmzUPZvwgA/edit#gid=974276133&fvid=1078495155)  
3. Match the batches we have available hamilton and flexmap information.  

**Note** 
It looks like the log was only started to collect after 2021-12-02   

raw .rmd file stored here 
```
/home/ddhillon/dyson-sync/projects/beta-av-testing/notebooks/process-pseudo-guardbanding/notebooks/02.rmd
```



##  Data Import 


### xMAP Data 


**Using data uptill 25th January**   

```{r warning=FALSE, message=FALSE}
raw <- read_csv(here::here("data", "raw", "beta-lot-stds-controls-2022-01-25.csv")) %>% 
    filter(!grepl("20211028_Reproducibilit_Panel2_Plate3", file_name)) %>% 
  filter(assay %in% c("WFDC2", "TNC", "FLT3L", "CEA", "IL-8", 
    "IL-1 R2", "MUC-16"))

```
**Batches in xMAP**    

```{r}
raw <- raw %>% 
  mutate(batch = str_remove(file_name, "_[0-9]+.csv")) %>% 
  mutate(batch = stringi::stri_replace_all_regex(batch, "\\d+$", "")) %>% 
  mutate(batch = stringi::stri_replace_all_regex(batch, "\\_$", "")) 

raw %>% 
  distinct(batch) %>% 
  DT::datatable(.)
```


```{r}
xmap_batches <- raw %>% 
   #mutate(batch = stringi::stri_replace_all_regex(batch, "\\d+$", "")) %>% 
   #mutate(batch = stringi::stri_replace_all_regex(batch, "\\_$", "")) %>% 
   distinct(batch)
```



###  Log of instruments 

```{r}
googlesheets4::gs4_auth()
```

```{r warning=FALSE, message=FALSE}
log <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1apRR9pYI0JXyZnKiISMVLC10kFAJ7Bp7KrmzUPZvwgA/edit#gid=974276133&fvid=1078495155", 
                          sheet = 2) %>% 
  janitor::clean_names() %>% 
  rename(batch = batch_name)
```


**Batches in log**    
```{r}
log_batches <- log %>% 
  distinct(batch)
log %>% 
    DT::datatable(.)
```
**Match the log of batches with the batches from xMAP data**   

*Which ones match?*  

```{r}
xmap_batches %>% 
  inner_join(log_batches) %>% 
    DT::datatable(.)
```
*Which ones don't match?*    

```{r}
log_batches %>% 
  anti_join(xmap_batches) %>% 
    DT::datatable(.)  

```
Some don't match since the names aren't exactly the same - we will change these manually. There are still some we're not able to retrieve xmap data on.  

```{r eval=FALSE, echo=TRUE}
xmap_batches %>% 
  mutate(batch = case_when(batch == "20211214_ShakeComp_Auto_Beta_Panel2_B3" ~ "20211214_ShakingCompare_Auto_Beta_Panel2", 
                           batch == "20211214_Shake_Workcell_Beta_Panel2_B1.csv" ~ "20211214_ShakingCompare_Workcell_Beta_Panel2", 
                           batch == "20211214_Shake_Workcell_Beta_Panel2_B2" ~ "20211214_ShakingCompare_Workcell_Beta_Panel2", 
                           batch == "20211214_Shake_Workcell_Beta_Panel2_B3" ~ "20211214_ShakingCompare_Workcell_Beta_Panel2", 
                           batch == "20211214_Shaking_Auto_Beta_Panel1_B1"  ~ "20211214_ShakingCompare_Auto_Beta_Panel1", 
                           batch == "20211214_Shaking_Auto_Beta_Panel1_B2" ~ "20211214_ShakingCompare_Auto_Beta_Panel1",
                           batch == "20211214_Shaking_Auto_Beta_Panel1_B3" ~ "20211214_ShakingCompare_Auto_Beta_Panel1", 
                           batch == "20211214_Shaking_Workcell_Beta_Panel1_B1" ~ "20211214_ShakingCompare_Workcell_Beta_Panel1", 
                           batch == "20211214_Shaking_Workcell_Beta_Panel1_B2" ~ "20211214_ShakingCompare_Workcell_Beta_Panel1", 
                           batch == "20211214_Shaking_Workcell_Beta_Panel1_B3" ~ "20211214_ShakingCompare_Workcell_Beta_Panel1", 
                           batch == "20210111_PltStd2_Panel1_P3_B1" ~ "20220111_PltStd2_Panel1_P3", 
                           batch == "20210111_PltStd2_Panel1_P3_B2" ~ "20220111_PltStd2_Panel1_P3", 
                           batch == "20210111_PltStd2_Panel1_P3_B3" ~ "20220111_PltStd2_Panel1_P3", 
                           batch == "20220111_PltStd2_Panel2_P3_B1" ~ "20220111_PltStd2_Panel2_P3", 
                           batch == "20220111_PltStd2_Panel2_P3_B2" ~ "20220111_PltStd2_Panel2_P3", 
                           batch == "20220111_PltStd2_Panel2_P3_B3" ~ "20220111_PltStd2_Panel2_P3", 
                           batch == "20220119_WC_P1vP6_P2_Plate2" ~ "20220119_WC_P1vP6_P2_plate2", 
                           TRUE ~ as.character(batch))) %>% 
  inner_join(log_batches)
```


**NOTE**     
Batches not in pate    
1. 20211221_DLS_Matrix_Int_  
2. 20220113_1500Shake_TS_  
3. 20220124_BufferAdditives_  
4. 20220201_AdditivesStds_  

Update the above plots after adding this in   



```{r}
xmap_batches <- xmap_batches %>% 
  mutate(batch = case_when(batch == "20211214_ShakeComp_Auto_Beta_Panel2_B3" ~ "20211214_ShakingCompare_Auto_Beta_Panel2", 
                           batch == "20211214_Shake_Workcell_Beta_Panel2_B1.csv" ~ "20211214_ShakingCompare_Workcell_Beta_Panel2", 
                           batch == "20211214_Shake_Workcell_Beta_Panel2_B2" ~ "20211214_ShakingCompare_Workcell_Beta_Panel2", 
                           batch == "20211214_Shake_Workcell_Beta_Panel2_B3" ~ "20211214_ShakingCompare_Workcell_Beta_Panel2", 
                           batch == "20211214_Shaking_Auto_Beta_Panel1_B1"  ~ "20211214_ShakingCompare_Auto_Beta_Panel1", 
                           batch == "20211214_Shaking_Auto_Beta_Panel1_B2" ~ "20211214_ShakingCompare_Auto_Beta_Panel1",
                           batch == "20211214_Shaking_Auto_Beta_Panel1_B3" ~ "20211214_ShakingCompare_Auto_Beta_Panel1", 
                           batch == "20211214_Shaking_Workcell_Beta_Panel1_B1" ~ "20211214_ShakingCompare_Workcell_Beta_Panel1", 
                           batch == "20211214_Shaking_Workcell_Beta_Panel1_B2" ~ "20211214_ShakingCompare_Workcell_Beta_Panel1", 
                           batch == "20211214_Shaking_Workcell_Beta_Panel1_B3" ~ "20211214_ShakingCompare_Workcell_Beta_Panel1", 
                           batch == "20210111_PltStd2_Panel1_P3_B1" ~ "20220111_PltStd2_Panel1_P3", 
                           batch == "20210111_PltStd2_Panel1_P3_B2" ~ "20220111_PltStd2_Panel1_P3", 
                           batch == "20210111_PltStd2_Panel1_P3_B1" ~ "20220111_PltStd2_Panel1_P3", 
                           batch == "20220111_PltStd2_Panel2_P3_B1" ~ "20220111_PltStd2_Panel2_P3", 
                           batch == "20220111_PltStd2_Panel2_P3_B2" ~ "20220111_PltStd2_Panel2_P3", 
                           batch == "20220111_PltStd2_Panel2_P3_B3" ~ "20220111_PltStd2_Panel2_P3", 
                           batch == "20220119_WC_P1vP6_P2_Plate2" ~ "20220119_WC_P1vP6_P2_plate2", 
                           TRUE ~ as.character(batch)))
```



Strings that are still not matching 
```{r}
log_batches %>% 
  #mutate(batch = case_when(grepl("PltStd2", batch ~ str_remove(batch, "(?<=Panel[0-9]).*")) %>% 
  anti_join(xmap_batches, by = "batch")   %>% 
  DT::datatable(.)

```



```{r}
## update the xmap file 
raw <- raw %>% 
  mutate(batch = case_when(batch == "20211214_ShakeComp_Auto_Beta_Panel2_B3" ~ "20211214_ShakingCompare_Auto_Beta_Panel2", 
                           batch == "20211214_Shake_Workcell_Beta_Panel2_B1.csv" ~ "20211214_ShakingCompare_Workcell_Beta_Panel2", 
                           batch == "20211214_Shake_Workcell_Beta_Panel2_B2" ~ "20211214_ShakingCompare_Workcell_Beta_Panel2", 
                           batch == "20211214_Shake_Workcell_Beta_Panel2_B3" ~ "20211214_ShakingCompare_Workcell_Beta_Panel2", 
                           batch == "20211214_Shaking_Auto_Beta_Panel1_B1"  ~ "20211214_ShakingCompare_Auto_Beta_Panel1", 
                           batch == "20211214_Shaking_Auto_Beta_Panel1_B2" ~ "20211214_ShakingCompare_Auto_Beta_Panel1",
                           batch == "20211214_Shaking_Auto_Beta_Panel1_B3" ~ "20211214_ShakingCompare_Auto_Beta_Panel1", 
                           batch == "20211214_Shaking_Workcell_Beta_Panel1_B1" ~ "20211214_ShakingCompare_Workcell_Beta_Panel1", 
                           batch == "20211214_Shaking_Workcell_Beta_Panel1_B2" ~ "20211214_ShakingCompare_Workcell_Beta_Panel1", 
                           batch == "20211214_Shaking_Workcell_Beta_Panel1_B3" ~ "20211214_ShakingCompare_Workcell_Beta_Panel1", 
                           batch == "20210111_PltStd2_Panel1_P3_B1" ~ "20220111_PltStd2_Panel1_P3", 
                           batch == "20210111_PltStd2_Panel1_P3_B2" ~ "20220111_PltStd2_Panel1_P3", 
                           batch == "20210111_PltStd2_Panel1_P3_B1" ~ "20220111_PltStd2_Panel1_P3", 
                           batch == "20220111_PltStd2_Panel2_P3_B1" ~ "20220111_PltStd2_Panel2_P3", 
                           batch == "20220111_PltStd2_Panel2_P3_B2" ~ "20220111_PltStd2_Panel2_P3", 
                           batch == "20220111_PltStd2_Panel2_P3_B3" ~ "20220111_PltStd2_Panel2_P3", 
                           batch == "20220119_WC_P1vP6_P2_Plate2" ~ "20220119_WC_P1vP6_P2_plate2", 
                           TRUE ~ as.character(batch)))

```


### Operator information?  

Can we also add in operator information to these experiments?  

```{r}
operator_data <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1xLCJMAVQLUytQBmNK6M7nUsd7EcBAPNQ2Fe1KVUZEMs/edit#gid=290693551", 
                                           sheet = "In-house_xMAP", skip = 8)
```

```{r}
operator_data %>% 
  select(Date, Operator, `Batch Name (in LIMS)`, Description, `Panel Name`, `Panel Lot #`, `Instrument Name`) %>% 
  janitor::clean_names() %>% 
  mutate(date = as.character(date)) %>% 
  mutate(date = lubridate::as_date(date)) %>% 
  filter(date >= "2021-12-02") %>% 
  rename(batch = batch_name_in_lims) %>% 
  inner_join(log_batches)

operator_batches <- operator_data %>% 
  select(Date, Operator, `Batch Name (in LIMS)`, Description, `Panel Name`, `Panel Lot #`, `Instrument Name`) %>% 
  janitor::clean_names() %>% 
  mutate(date = as.character(date)) %>% 
  mutate(date = lubridate::as_date(date)) %>% 
  filter(date >= "2021-12-02") %>% 
  rename(batch = batch_name_in_lims) %>% 
  select(operator, batch, description)
```






## Viz   


### QCs   

Which experiments had QCs on them?  
10 experiments?  

5 experiments had RCs on them (log was started on 20211202 so any experiments with RCs on them prior to that aren't in this list currently) 

We have more data on the latest controls so we will look at those  

```{r include=FALSE}
raw %>% 
  inner_join(log, by = "batch") %>% 
  inner_join(operator_batches)
```


```{r include=FALSE}
plot_data <- raw %>% 
  inner_join(log, by = "batch") %>% 
  inner_join(operator_batches) %>% 
  filter(grepl("QC", xponent_id)) %>% 
  filter(!grepl("MIF", xponent_id)) %>% 
  filter(!grepl("OPN", xponent_id)) %>% 
  filter(!grepl("THBS", xponent_id)) %>% 
  mutate(hamilton = ifelse(hamilton == "ProStar1", "ProStar 1", hamilton)) %>% 
  mutate(hamilton = ifelse(hamilton == "ProStar2", "ProStar 2", hamilton)) 

plot_data %>% 
  distinct(batch) %>% 
  DT::datatable(.)
```

```{r}
plot_data %>% 
  distinct(batch, .keep_all = TRUE) %>% 
  count(flex_map3d, hamilton, operator) %>% 
  mutate(n = as.character(n)) %>% 
  ggplot(.,aes(hamilton, flex_map3d)) + 
  geom_point(aes(color = n)) + 
  facet_grid(cols = vars(operator)) + 
  labs(subtitle = "Hard to make definitive comparisons with small number of experiments")
```


```{r}
plot_data <- raw %>% 
  inner_join(log, by = "batch") %>% 
  inner_join(operator_batches) %>% 
  filter(grepl("QC", xponent_id)) %>% 
  filter(!grepl("MIF", xponent_id)) %>% 
  filter(!grepl("OPN", xponent_id)) %>% 
  filter(!grepl("THBS", xponent_id)) %>% 
  mutate(hamilton = ifelse(hamilton == "ProStar1", "ProStar 1", hamilton)) %>% 
  mutate(hamilton = ifelse(hamilton == "ProStar2", "ProStar 2", hamilton)) %>% 
  mutate(xponent_id = str_remove(xponent_id, " "))
```



**Plots out all the RCs for each flexmap and hamilton**   

```{r}
list_of_proteins <- plot_data %>% distinct(assay) %>% pull()
```



```{r}
assay_level_plot_function <- function(protein = "NULL", x_axis = flex_map3d, 
                                      color = hamilton) {
  p <- plot_data %>% 
  filter(assay == protein) %>% 
  group_by(assay, xponent_id, batch, flex_map3d, hamilton, operator) %>% 
  summarise(avg_conc = mean(calc_conc, na.rm = TRUE)) %>% 
  ggplot(.,aes(x = {{x_axis}}, y = avg_conc, operator = operator)) + 
  geom_point(aes( color = {{color}})) + 
  facet_grid(cols = vars(xponent_id)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 5), 
        strip.text = element_text(
    size = 5, color = freenome_colors[1])) 

ggplotly(p)
}

rc_plots <- map(list_of_proteins, ~ assay_level_plot_function(.x))

render_plot <- function(x) {
  p <- rc_plots[x]
  cat("\n")
    cat(htmltools::renderTags(as.widget(p))$html)
}


tabset_rendering <- function(x) {
  cat("##### ", list_of_proteins[x], "\n") 
  
  render_plot(x)

}
```
  
#### Flexmap x-axis {.tabset}  

```{r fig.height=14, fig.width=12, results='asis'}
purrr::map(1:length(list_of_proteins), ~ tabset_rendering(x = .x))
```

#### Hamilton x-axis {.tabset}  


```{r}
## plot hamilton on x-axis instead 
rc_plots <- map(list_of_proteins, ~ assay_level_plot_function(.x, x_axis = hamilton, 
                                                              color = flex_map3d))
```


```{r results='asis', fig.height=14, fig.width=12}
purrr::map(1:length(list_of_proteins), ~ tabset_rendering(x = .x))
```


```{r echo=FALSE, messages=FALSE, warning=FALSE, eval=TRUE}
# Attach the Dependencies since they do not get included with renderTags(...)$html
deps <- lapply(
  Filter(f = function(x){inherits(x,"htmlwidget")}, x = rc_plots),
  function(hw){
    htmltools::renderTags(hw)$dependencies
  }
)
htmltools::attachDependencies(x = htmltools::tagList(), value = unlist(deps,recursive=FALSE))
```



### Recoveries  

Experiments with recoveries  

```{r}
plot_data <- raw %>% 
  inner_join(log, by = "batch") %>% 
  filter(sample_type == "standard") %>% 
  inner_join(operator_batches) %>% 
  mutate(hamilton = ifelse(hamilton == "ProStar1", "ProStar 1", hamilton)) %>% 
  mutate(hamilton = ifelse(hamilton == "ProStar2", "ProStar 2", hamilton)) %>% 
  filter(pct_recovery < 200)

plot_data %>% 
  distinct(batch) %>% 
  DT::datatable(.)

plot_data %>% 
  distinct(batch, .keep_all = TRUE) %>% 
  count(hamilton, flex_map3d, operator) %>% 
  ggplot(., aes(hamilton, flex_map3d)) + 
  geom_point(aes(color = as.character(n))) +
  facet_grid(cols = vars(operator))
```




```{r}
recovery_plot_function <- function(protein = "NULL", x_axis = flex_map3d, 
                                      color = hamilton) {
  p <- plot_data %>% 
  filter(assay == protein) %>% 
  group_by(assay, xponent_id, batch, flex_map3d, hamilton, operator) %>% 
  summarise(avg_recovery = mean(pct_recovery, na.rm = TRUE)) %>% 
  ggplot(.,aes(x = {{x_axis}}, y = avg_recovery, operator = operator)) + 
  geom_point(aes( color = {{color}})) + 
  facet_grid(cols = vars(xponent_id)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(
    size = 10, color = freenome_colors[3])) 

ggplotly(p)
}

recovery_plots <- map(list_of_proteins, ~ recovery_plot_function(.x))

render_plot <- function(x) {
  p <- recovery_plots[x]
  cat("\n")
    cat(htmltools::renderTags(as.widget(p))$html)
}


tabset_rendering <- function(x) {
  cat("##### ", list_of_proteins[x], "\n") 
  
  render_plot(x)

}
```
  
#### Flexmap x-axis {.tabset}  

```{r fig.height=14, fig.width=12, results='asis'}
purrr::map(1:length(list_of_proteins), ~ tabset_rendering(x = .x))
```

#### Hamilton x-axis {.tabset}  


```{r}
## plot hamilton on x-axis instead 
recovery_plots <- map(list_of_proteins, ~ recovery_plot_function(.x, x_axis = hamilton, 
                                                              color = flex_map3d))
render_plot <- function(x) {
  p <- recovery_plots[x]
  cat("\n")
    cat(htmltools::renderTags(as.widget(p))$html)
}
```


```{r results='asis', fig.height=14, fig.width=12}
purrr::map(1:length(list_of_proteins), ~ tabset_rendering(x = .x))
```



```{r echo=FALSE, messages=FALSE, warning=FALSE, eval=TRUE}
# Attach the Dependencies since they do not get included with renderTags(...)$html
deps <- lapply(
  Filter(f = function(x){inherits(x,"htmlwidget")}, x = recovery_plots),
  function(hw){
    htmltools::renderTags(hw)$dependencies
  }
)
htmltools::attachDependencies(x = htmltools::tagList(), value = unlist(deps,recursive=FALSE))
```

#### Operator specific comparison  {.tabset}

```{r}
plot_data %>% 
  distinct(batch, .keep_all = TRUE) %>% 
  count(hamilton, flex_map3d, operator) %>% 
  ggplot(., aes(hamilton, flex_map3d)) + 
  geom_point(aes(color = as.character(n))) +
  facet_grid(cols = vars(operator)) + 
  labs(title = "Should only compare difference within one operator?")
```

```{r}
plot_data <- plot_data %>% 
  filter(operator == "Wilson Z")
```



```{r}
## plot flexmap on x-axis instead 
recovery_plots <- map(list_of_proteins, ~ recovery_plot_function(.x, x_axis = flex_map3d, 
                                                              color = hamilton))
render_plot <- function(x) {
  p <- recovery_plots[x]
  cat("\n")
    cat(htmltools::renderTags(as.widget(p))$html)
}
```


```{r results='asis', fig.height=12, fig.width=8}
purrr::map(1:length(list_of_proteins), ~ tabset_rendering(x = .x))
```








### Bead counts  


```{r}
plot_data <- raw %>% 
  inner_join(log, by = "batch") %>% 
  inner_join(operator_batches) %>% 
  mutate(hamilton = ifelse(hamilton == "ProStar1", "ProStar 1", hamilton)) %>% 
  mutate(hamilton = ifelse(hamilton == "ProStar2", "ProStar 2", hamilton)) 
```

```{r}
bead_count_plot_function <- function(protein = "NULL", x_axis = flex_map3d, 
                                      color = hamilton) {
  p <- plot_data %>% 
  filter(assay == protein) %>% 
  group_by(assay, sample_type, batch, flex_map3d, hamilton, operator) %>% 
  summarise(avg_bead = mean(bead_count, na.rm = TRUE)) %>% 
  ggplot(.,aes(x = {{x_axis}}, y = avg_bead, operator = operator)) + 
  geom_point(aes( color = {{color}})) + 
  facet_grid(cols = vars(sample_type)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

ggplotly(p)
}

bead_plots <- map(list_of_proteins, ~ bead_count_plot_function(.x))
```
```{r}

render_plot <- function(x) {
  p <- bead_plots[x]
  cat("\n")
    cat(htmltools::renderTags(as.widget(p))$html)
}


tabset_rendering <- function(x) {
  cat("##### ", list_of_proteins[x], "\n") 
  
  render_plot(x)

}
```

  
#### Flexmap x-axis {.tabset}  

```{r eval=FALSE, fig.height=12, fig.width=8, include=FALSE, results='asis'}
purrr::map(1:length(list_of_proteins), ~ tabset_rendering(x = .x))
```

#### Hamilton x-axis {.tabset}  


```{r}
## plot hamilton on x-axis instead 
bead_plots <- map(list_of_proteins, ~ bead_count_plot_function(.x, x_axis = hamilton, 
                                                              color = flex_map3d))

render_plot <- function(x) {
  p <- bead_plots[x]
  cat("\n")
    cat(htmltools::renderTags(as.widget(p))$html)
}
```


```{r results='asis', fig.height=12, fig.width=8}
purrr::map(1:length(list_of_proteins), ~ tabset_rendering(x = .x))
```























