---
title: "Failure Modes"
author: "Dilsher Singh Dhillon"
date: "`r format(Sys.time(),'%d %B,%Y')`"
output:
  html_document:
    toc: true
    toc_float : true 
---
<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: #948DFF;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```


```{r}
library(tidyverse) 
```

```{r}
freenome_colors <- c('#948DFF', '#1DE3FE', '#BBD532', '#FF9D42',  '#FC2E7B', 
                   '#FECDD1')
```

```{r eval=FALSE, include=FALSE}
library(googleCloudStorageR)
googleAuthR::gar_gce_auth()
gcs_get_object("gs://inhouse-xmap-data/user_data_frames/betalot_experiments-2022-02-21.csv", saveToDisk="/home/ddhillon/projects/beta-av-testing/data/raw/beta-lot-stds-controls-2022-02-21.csv", 
               overwrite = TRUE)
```



## PATE import 

Use these set of commands to import the data

```
pate-rnd xmap-collector --include_file_str 20220119_WC_P1vP6 \
  --include_file_str  20220120_ShakeSpd_1000rpm_Panel1_Plate1 \
  --include_file_str  20220120_ShakeSpd_1200rpm_Panel1_Plate2 \
  --include_file_str  20220120_ShakeSpd_1500rpm_Panel1_Plate3 \
  --include_file_str  20220120_ShakeSpd_1000rpm_Panel2_Plate1 \
  --include_file_str  20220120_ShakeSpd_1200rpm_Panel2_Plate2 \
  --include_file_str  20220120_ShakeSpd_1500rpm_Panel2_Plate3 \
  --include_file_str  20220120_ShakeSpd_1200rpm_Panel2_Plate2 \
  --include_file_str  20220120_ShakeSpd_1500rpm_Panel2_Plate2 \
  --include_file_str  Beta \
  --include_file_str  Interf \
  --include_file_str  PltStd \
  --include_file_str  Endogenous \
  --include_file_str  Exogenous \
  --include_file_str  Platinum \
  --include_file_str  Reproducibility \
  --include_file_str  Donor_Screening \
  --include_file_str  PlatinumStd \
  --include_file_str  HamiltonEquiv\
  --include_file_str  ShakingCompare \
  --include_file_str  20211221_DLS_Matrix_Int \
  --include_file_str  20220124_BufferAdditives \
  --include_file_str  20220208_CRC_EDTA \
  --include_file_str  Matrix_Buffer_TritonX \
  --include_file_str  20220215_WCFunctional \
  --include_file_str  20220217_Linearity_Streck \
  --include_sample_str Standard --include_sample_str Buffer --include_sample_str Background --include_sample_str QC --include_sample_str RC  --ignore_case_sample \
  --out_file_name betalot_experiments-2022-02-21.csv
```


```
gsutil cp gs://inhouse-xmap-data/user_data_frames/betalot_experiments-2022-02-21.csv /home/ddhillon/projects/beta-av-testing/data/raw/beta-lot-stds-controls-2022-02-21.csv
```



## Data 

Which experiments are we looking at? 

```{r}
raw <- read_csv(here::here("data", "raw", "beta-lot-stds-controls-2022-02-21.csv")) # nolint

raw <- raw %>% 
  mutate(batch = str_remove(file_name, "_[0-9]+.csv")) %>% 
  filter(!grepl("20211028_Reproducibilit_Panel2_Plate3", file_name)) %>% 
   mutate(experiment_date = str_extract(batch, "[0-9]+_")) %>% 
  mutate(experiment_date = str_extract(batch, "[0-9]+")) %>% 
  mutate(experiment_date = lubridate::as_date(experiment_date, format = "%Y%d%m")) %>% 
  mutate(month = lubridate::month(experiment_date), 
         year = lubridate::year(experiment_date))

raw %>% 
  count(year)
raw %>% 
  count(experiment_date)

raw %>% 
  #filter(experiment_date == "2021-02-12" | experiment_date == "2021-11-01") %>% 
  distinct(batch)
n_batches <- nrow(raw %>% distinct(batch))
```


```{r}
bead_data <- raw %>% 
  filter(assay %in% c("WFDC2", "CEA", "IL-8", "IL-1 R2", "TNC", "MUC-16", "FLT3L"))

bead_data %>% 
  count(batch) %>% 
  DT::datatable()
```

## Viz 

**% Bead count failures across all experiments?** 

```{r}
bead_data %>% 
  filter(sample_type == "standard") %>% 
  mutate(bead_fail = ifelse(bead_count < 35, 1, 0)) %>% 
  group_by(assay, xponent_id) %>% 
  summarise(mean_fails = 100*mean(bead_fail)) %>% 
  ggplot(.,aes(xponent_id, mean_fails)) + 
  geom_point(color = freenome_colors[1]) + 
  facet_wrap(vars(assay)) + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  labs(title = "% of Bead Count failures")
```

Exclude experiments that had the standards mixed with salts (doesn't reflect normal process) 

```{r}
bead_data %>% 
  filter(sample_type == "standard") %>% 
  filter(!grepl("Salt", xponent_id)) %>% 
  mutate(bead_fail = ifelse(bead_count < 35, 1, 0)) %>% 
  group_by(assay, xponent_id) %>% 
  summarise(mean_fails = 100*mean(bead_fail)) %>% 
  ggplot(.,aes(xponent_id, mean_fails)) + 
  geom_point(color = freenome_colors[1]) + 
  facet_wrap(vars(assay)) + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  labs(title = "% of Bead Count failures")
```




**How many outliers AFTER bead failure?**   

```{r}
mod_z_calc <- function(x_vec) {
  x_vec_median <- median(x_vec, na.rm = TRUE) 
  x_vec_mad <- mad(x_vec, na.rm = TRUE)
  
  mod_z <- 0.6745*(x_vec - x_vec_median)/x_vec_mad
  return(mod_z)
  
}

bead_data %>% 
  filter(sample_type == "standard") %>% 
  filter(!grepl("Salt", xponent_id)) %>% 
  mutate(bead_fail = ifelse(bead_count < 35, 1, 0)) %>% 
  filter(bead_fail == 0) %>% 
  group_by(xponent_id, assay, file_name) %>% 
  mutate(mod_z = mod_z_calc(median_mfi)) %>% 
  mutate(outlier = ifelse(abs(mod_z) > 3.5, 1, 0)) %>% 
  ungroup() %>% 
  group_by(assay, xponent_id) %>% 
  summarise(mean_fails = 100*mean(outlier)) %>% 
  ggplot(.,aes(xponent_id, mean_fails)) + 
  geom_point(color = freenome_colors[1]) + 
  facet_wrap(vars(assay)) + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  labs(title = "% of Outlier", 
       y = "% of Outliers")


```

## Scenarios  

There are 3 ways we could be left with 2 replicates in a given standard  

Can we find out how many times the following occurred in our historical data? 

1. Bead count failed AND after removing that well, there was still an outlier?  
2. How many times there were bead failures in the same batch and same standard?  
3. After removing the bead fails, how many times does it occur that there are 2 outliers in a standard? 


**1**   

~ 5 % of the time 

```{r}
bead_fail_wells <- bead_data %>% 
  filter(sample_type == "standard") %>% 
  mutate(bead_fail = ifelse(bead_count < 35, 1, 0)) %>% 
  filter(bead_fail == 1)


outlier_wells <- bead_data %>% 
  filter(sample_type == "standard") %>% 
  mutate(bead_fail = ifelse(bead_count < 35, 1, 0)) %>% 
  filter(bead_fail == 0) %>% 
  group_by(xponent_id, assay, file_name) %>% 
  mutate(mod_z = mod_z_calc(median_mfi)) %>% 
  mutate(outlier = ifelse(abs(mod_z) > 3.5, 1, 0)) %>% 
  ungroup() %>% 
  filter(outlier == 1) %>% 
  select(-bead_fail)

outlier_wells %>% 
  filter(file_name == "20211129_PltStd_ProdLot_Panel1_B1_20211130_125634.csv") 

number_1_experiments <- bead_fail_wells %>% 
  inner_join(outlier_wells, by = c("assay", "file_name", "xponent_id")) %>% 
  select(assay, file_name, outlier, bead_fail, xponent_id) 
number_1_experiments
100*(nrow(number_1_experiments)/n_batches)
```

**2**  
How many plates where at least one standard had > 1 bead fail   

~ 9 % of the time 
 
```{r}
number_2_experiemnts <- bead_data %>% 
  filter(sample_type == "standard") %>% 
  mutate(bead_fail = ifelse(bead_count < 35, 1, 0)) %>% 
  filter(bead_fail == 1) %>% 
  count(batch, xponent_id, assay) %>% 
  filter(n > 1) %>% 
  distinct(batch)

number_2_experiemnts
100*(nrow(number_2_experiemnts)/n_batches)
```



**3**   

After removing the bead fails, how many times does it occur that there are 2 outliers in a standard? 

~12 % of the time 

```{r}
number_3_experiments <- bead_data %>% 
  filter(sample_type == "standard") %>% 
  mutate(bead_fail = ifelse(bead_count < 35, 1, 0)) %>% 
  filter(bead_fail == 0) %>% 
  group_by(xponent_id, assay, file_name) %>% 
  mutate(mod_z = mod_z_calc(median_mfi)) %>% 
  mutate(outlier = ifelse(abs(mod_z) > 3.5, 1, 0)) %>% 
  ungroup() %>% 
  filter(outlier == 1) %>% 
  count(batch, xponent_id, assay) %>% 
  filter(n > 1) %>% 
  distinct(batch)
number_3_experiments
100*(nrow(number_3_experiments)/n_batches)
```





#### Sample dependent failure   

```{r eval=FALSE, include=FALSE}
 bead_data %>% 
  filter(grepl("RC", xponent_id) | grepl("QC", xponent_id)) %>% 
  mutate(bead_fail = ifelse(bead_count < 35, 1, 0)) %>% 
  filter(bead_fail == 1) %>% 
  count(xponent_id, batch, bead_fail) %>% 
  ggplot(.,aes(xponent_id, n)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 

 bead_data %>% 
  filter(grepl("RC", xponent_id) | grepl("QC", xponent_id)) %>% 
  mutate(bead_fail = ifelse(bead_count < 35, 1, 0)) %>% 
  filter(bead_fail == 1) %>% 
  count(xponent_id, batch, bead_fail) %>% 
  filter(n > 2) %>% 
  distinct(batch) 
  ggplot(.,aes(xponent_id, n)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) 
  
  bead_data %>% 
    count(batch)
```
