---
title: "QC-Strategy-Simulation"
output:
  html_document:
    df_print: paged
---


### Introduction    









Explore the following 2 rules in different situations  
1. 13S rule  

2. R4S-like: two measurements (across levels for the same assay) in the same batch have a 4 standard deviation difference (such as one exceeding 2 SD above the mean, and another exceeding 2 SD below the mean)   

3. Two or measurements (across levels for the same assay) in the same batch have exceeded 2 standard deviations on the same side of the mean   




```{r}
library(mvtnorm)
library(tidyverse)
library(furrr)
```

```{r}
plan(multisession, workers = 6)
```


```{r}
freenome_colors <- c('#948DFF', '#1DE3FE', '#BBD532', '#FF9D42',  '#FC2E7B', 
                   '#FECDD1')
```



```{r}
proteins <- 7  
controls <- 3  
```


#### Rule 1  

2 controls exceeding 3SD in either direction. 

```{r eval=FALSE, include=FALSE}
mean_vec <- c(rnorm(1), 3 * rnorm(1), 6 * rnorm(1))
sigma_vec <-
  c(rnorm(1, 1, 0.05), 3 * rnorm(1, 1, 0.05), 5 * rnorm(1, 1, 0.05))
variance_vec <- sigma_vec ^ 2

rho <- 0.4 ## moderate correlation



cov_matrix <-
  matrix(
    c(
      variance_vec[1],
      rho * sigma_vec[1] * sigma_vec[2],
      rho * sigma_vec[1] * sigma_vec[3],
      rho * sigma_vec[1] * sigma_vec[2],
      variance_vec[2],
      rho * sigma_vec[2] * sigma_vec[3],
      rho * sigma_vec[1] * sigma_vec[3],
      rho * sigma_vec[2] * sigma_vec[3],
      variance_vec[3]
    ),
    nrow = 3,
    ncol = 3
  )




#Using these above, we 
# 1. Generate 20 samples from the multivariate normal distribution   
# 2. Calculate the 3SD limit  

#**1**   

measurands <- rmvnorm(20, mean = mean_vec, sigma = cov_matrix)




#**2**   

sd_limits <- apply(measurands, MARGIN = 2, FUN = sd)
mean_limit <- apply(measurands, MARGIN = 2, FUN = mean)

# Generate 1000 RVs 7 times or generate 7000 RVs?  


sim_measurands <- rmvnorm(1e3, mean = mean_vec, sigma = cov_matrix)

#tmp <- replicate(7, rmvnorm(1e3, mean = mean_vec, sigma = cov_matrix))

sim_measurands %>% 
  data.frame() %>% 
  rename(x = X1, y = X2, z = X3) %>% 
  mutate(x_3sd = case_when(x >  + 3*sd_limits[1] | x < x - 3*sd_limits[1] ~ 1, 
                                  is.double(x) ~ 0), 
         y_3sd = case_when(y > y + 3*sd_limits[2] | y < y - 3*sd_limits[2] ~ 1, 
                                  is.double(y) ~ 0), 
         z_3sd = case_when(z > z + 3*sd_limits[3] | z < z -3*sd_limits[3] ~ 1,
                                  is.double(z) ~ 0)) %>% 
  mutate(total_sd = x_3sd + y_3sd + z_3sd) %>% 
  filter(total_sd >= 1) %>% 
  nrow(.)/(nrow(sim_measurands)/100)
```



**function for 13s**   

```{r}
single_13s_simulation <-
  function(correlation = 0.4,
           n = 20,
           batches = 1000,
           proteins = 7) {
    mean_vec <- c(rnorm(1), 3 * rnorm(1), 6 * rnorm(1))
    sigma_vec <-
      c(rnorm(1, 1, 0.05), 3 * rnorm(1, 1, 0.05), 5 * rnorm(1, 1, 0.05))
    variance_vec <- sigma_vec ^ 2
    
    rho <- correlation ## moderate correlation
    
    cov_matrix <-
      matrix(
        c(
          variance_vec[1],
          rho * sigma_vec[1] * sigma_vec[2],
          rho * sigma_vec[1] * sigma_vec[3],
          rho * sigma_vec[1] * sigma_vec[2],
          variance_vec[2],
          rho * sigma_vec[2] * sigma_vec[3],
          rho * sigma_vec[1] * sigma_vec[3],
          rho * sigma_vec[2] * sigma_vec[3],
          variance_vec[3]
        ),
        nrow = 3,
        ncol = 3
      )
    
    ## generate spec limits
    measurands <- rmvnorm(n, mean = mean_vec, sigma = cov_matrix)
    sd_limits <- apply(measurands, MARGIN = 2, FUN = sd)
    mean_limit <- apply(measurands, MARGIN = 2, FUN = mean)

    # Generate 1000 RVs 7 times or generate 7000 RVs?
    
    sim_measurands <-
      rmvnorm(batches, mean = mean_vec, sigma = cov_matrix)
    
    num_times <- sim_measurands %>%
      data.frame() %>%
      rename(x = X1, y = X2, z = X3) %>%
      mutate(x_upper = mean_limit[1] + 3 * sd_limits[1], 
             x_lower = mean_limit[1] - 3 * sd_limits[1], 
             y_upper = mean_limit[2] + 3 * sd_limits[2], 
             y_lower = mean_limit[2] - 3 * sd_limits[2], 
             z_upper = mean_limit[3] + 3 * sd_limits[3], 
             z_lower = mean_limit[3] - 3 * sd_limits[3]) %>% 
      mutate(
        x_3sd = case_when(x > x_upper | x < x_lower ~ 1,
                          is.double(x) ~ 0),
        y_3sd = case_when(y > y_upper |
                            y < y_lower ~ 1,
                          is.double(y) ~ 0),
        z_3sd = case_when(z > z_upper |
                            z < z_lower ~ 1,
                          is.double(z) ~ 0)
      ) %>%
      mutate(total_sd = x_3sd + y_3sd + z_3sd) %>%
      filter(total_sd >= 1) %>%
      nrow(.) / (batches / 100)
    return(num_times*proteins)
  }

```

**Iteration over multiple correlations and initial data generation**   

```{r}
parameters <- tidyr::crossing(correlation = seq(0.2, 0.8, by = 0.1), 
                n = seq(10, 50, by = 5))
```


```{r}
iterate_over_params <- function(params = parameters, i = 1) {
  imap_dbl(1:1000, ~single_13s_simulation(correlation = parameters$correlation[i], 
                                            n = parameters$n[i])) %>% 
    mean()
}


fps_13s <- furrr::future_imap_dbl(1:nrow(parameters), ~ 
                                    iterate_over_params(params = parameters, 
                                                   i = .x), 
                              .options = furrr_options(seed = TRUE))
```

```{r}
fps_13s %>% 
  data.frame() %>% 
  janitor::clean_names() %>% 
  rename(fp_rate = x) %>% 
  bind_cols(parameters) %>% 
  rename(number_experiments = n) %>% 
  ggplot(.,aes(correlation, fp_rate)) + 
  geom_point(aes(color = number_experiments), 
             size = 2.5) + 
  scale_color_gradientn(colors = c(freenome_colors[1], 
                                   freenome_colors[2], 
                                   freenome_colors[3])) + 
  theme_classic() + 
  labs(title = "False alarm % ", 
       subtitle = "Function of correlation and batches(n) used to set limits")
```




#### Rule 3   

```{r eval=FALSE, include=FALSE}

```



Let's write a function for simulating the data  

##### Assumptions   

1. One assay, 3 controls 
  a. **Mean**  
  Med control = 3*Low Control  
  High control = 6*Low Control  
  b. **Variance**  
  Assume similar distribution for variance of each control (over optimisitic - low controls tend to be more noisy?)   

2. Correlation - explored a range of positive correlations  
3. Batches used to set the spec limits  - explored 10 - 30  


```{r}
single_assay_simulation <-
  function(correlation = 0.4,
           n = 20,
           batches = 1000, proteins = 7) {
    mean_vec <- c(rnorm(1), 3 * rnorm(1), 6 * rnorm(1))
    sigma_vec <-
      c(rnorm(1, 1, 0.05), 3 * rnorm(1, 1, 0.05), 5 * rnorm(1, 1, 0.05))
    variance_vec <- sigma_vec ^ 2
    
    rho <- correlation ## moderate correlation
    
    cov_matrix <-
      matrix(
        c(
          variance_vec[1],
          rho * sigma_vec[1] * sigma_vec[2],
          rho * sigma_vec[1] * sigma_vec[3],
          rho * sigma_vec[1] * sigma_vec[2],
          variance_vec[2],
          rho * sigma_vec[2] * sigma_vec[3],
          rho * sigma_vec[1] * sigma_vec[3],
          rho * sigma_vec[2] * sigma_vec[3],
          variance_vec[3]
        ),
        nrow = 3,
        ncol = 3
      )
    
    ## generate spec limits
    measurands <- rmvnorm(n, mean = mean_vec, sigma = cov_matrix)
    sd_limits <- apply(measurands, MARGIN = 2, FUN = sd)
    mean_limit <- apply(measurands, MARGIN = 2, FUN = mean)
    # Generate 1000 RVs 7 times or generate 7000 RVs?
    
    sim_measurands <-
      rmvnorm(batches, mean = mean_vec, sigma = cov_matrix)
    
    num_times <- sim_measurands %>%
      data.frame() %>%
      rename(x = X1, y = X2, z = X3) %>%
      mutate(x_upper = mean_limit[1] + 2 * sd_limits[1], 
             x_lower = mean_limit[1] - 2 * sd_limits[1], 
             y_upper = mean_limit[2] + 2 * sd_limits[2], 
             y_lower = mean_limit[2] - 2 * sd_limits[2], 
             z_upper = mean_limit[3] + 2 * sd_limits[3], 
             z_lower = mean_limit[3] - 2 * sd_limits[3]) %>% 
      mutate(
        x_2sd = case_when(x > x_upper ~ 1,
                          x < x_lower ~ -1,
                          is.double(x) ~ 0),
        y_2sd = case_when(y > y_upper ~ 1,
                          y < y_lower ~ -1,
                          is.double(y) ~ 0),
        z_2sd = case_when(z > z_upper ~ 1,
                          z < z_lower ~ -1,
                          is.double(z) ~ 0)
      ) %>%
      mutate(total_sd = x_2sd + y_2sd + z_2sd) %>%
      filter(total_sd >= 2) %>%
      nrow(.) / (batches / 100)
    return(num_times*proteins)
  }

```

**Iteration over multiple correlations and initial data generation**   

```{r}
parameters <- tidyr::crossing(correlation = seq(0.2, 0.8, by = 0.1), 
                n = seq(10, 50, by = 5))
```


```{r}
iterate_over_params <- function(params = parameters, i = 1) {
  imap_dbl(1:1000, ~single_assay_simulation(correlation = parameters$correlation[i], 
                                            n = parameters$n[i])) %>% 
    mean()
}


fps <- furrr::future_imap_dbl(1:nrow(parameters), ~ iterate_over_params(params = parameters, 
                                                   i = .x), 
                              .options = furrr_options(seed = TRUE))
```


```{r}
fps %>% 
  data.frame() %>% 
  janitor::clean_names() %>% 
  rename(fp_rate = x) %>% 
  bind_cols(parameters) %>% 
  rename(number_experiments = n) %>% 
  ggplot(.,aes(correlation, fp_rate)) + 
  geom_point(aes(color = number_experiments), 
             size = 2.5) + 
  scale_color_gradientn(colors = c(freenome_colors[1], 
                                   freenome_colors[2], 
                                   freenome_colors[3])) + 
  theme_classic() + 
  labs(title = "False alarm % for single assay(Rule 2)", 
       subtitle = "Function of correlation and batches(n) used to set limits")
```






#### Rule 2    

We will count the number of times any of these occurs  

1. X > 2SD and Y < 2SD 
2. X > 2SD and Z < 2SD  
3. X < 2SD and Y > 2SD  
4. X < 2SD and Z > 2SD  
5. Y < 2SD and Z > 2SD 
6. Y > 2SD and Z < 2SD   


```{r}
r4s_assay_simulation <-
  function(correlation = 0.4,
           n = 20,
           batches = 1000, 
           proteins = 7) {
    mean_vec <- c(rnorm(1), 3 * rnorm(1), 6 * rnorm(1))
    sigma_vec <-
      c(rnorm(1, 1, 0.05), 3 * rnorm(1, 1, 0.05), 5 * rnorm(1, 1, 0.05))
    variance_vec <- sigma_vec ^ 2
    
    rho <- correlation ## moderate correlation
    
    cov_matrix <-
      matrix(
        c(
          variance_vec[1],
          rho * sigma_vec[1] * sigma_vec[2],
          rho * sigma_vec[1] * sigma_vec[3],
          rho * sigma_vec[1] * sigma_vec[2],
          variance_vec[2],
          rho * sigma_vec[2] * sigma_vec[3],
          rho * sigma_vec[1] * sigma_vec[3],
          rho * sigma_vec[2] * sigma_vec[3],
          variance_vec[3]
        ),
        nrow = 3,
        ncol = 3
      )
    
    ## generate spec limits
    measurands <- rmvnorm(n, mean = mean_vec, sigma = cov_matrix)
    sd_limits <- apply(measurands, MARGIN = 2, FUN = sd)
    mean_limit <- apply(measurands, MARGIN = 2, FUN = mean) 
    # Generate 1000 RVs 7 times or generate 7000 RVs?
    
    sim_measurands <-
      rmvnorm(batches, mean = mean_vec, sigma = cov_matrix)
    
    
    num_times <- sim_measurands %>%
      data.frame() %>%
      rename(x = X1, y = X2, z = X3) %>%
      mutate(x_upper = mean_limit[1] + 2 * sd_limits[1], 
             x_lower = mean_limit[1] - 2 * sd_limits[1], 
             y_upper = mean_limit[2] + 2 * sd_limits[2], 
             y_lower = mean_limit[2] - 2 * sd_limits[2], 
             z_upper = mean_limit[3] + 2 * sd_limits[3], 
             z_lower = mean_limit[3] - 2 * sd_limits[3]) %>% 
      mutate(
        x_2sd = case_when(x > x_upper ~ 1,
                          x < x_lower ~ -1,
                          is.double(x) ~ 0),
        y_2sd = case_when(y > y_upper ~ 1,
                          y < y_lower ~ -1,
                          is.double(y) ~ 0),
        z_2sd = case_when(z > z_upper ~ 1,
                          z < z_lower ~ -1,
                          is.double(z) ~ 0)
      ) %>%
      mutate(
        sd_4_opposite = case_when(
          x_2sd == 1 & y_2sd == -1 ~ "yes",
          x_2sd == 1 &
            z_2sd == -1 ~ "yes",
          x_2sd == -1 &
            y_2sd == 1 ~ "yes",
          x_2sd == -1 &
            z_2sd == 1 ~ "yes",
          y_2sd == -1 &
            z_2sd == 1 ~ "yes",
          y_2sd == 1 &
            z_2sd == -1 ~ "yes"
        )
      ) %>%
      filter(sd_4_opposite == "yes") %>%
      nrow(.) / (batches / 100)
    
    return(num_times*proteins)
    
  }
```



```{r}
r4s_iterate_over_params <- function(params = parameters, i = 1) {
  imap_dbl(1:1000, ~r4s_assay_simulation(correlation = parameters$correlation[i], 
                                            n = parameters$n[i])) %>% 
    mean()
}


r4s_fps <- furrr::future_imap_dbl(1:nrow(parameters), ~ r4s_iterate_over_params(params = parameters, 
                                                   i = .x), 
                                  .options = furrr_options(seed = TRUE))
```

R4S-like: two measurements (across levels for the same assay) in the same batch have a 4 standard deviation difference (such as one exceeding 2 SD above the mean, and another exceeding 2 SD below the mean).
Two or measurements (across levels for the same assay) in the same batch have exceeded 2 standard deviations on the same side of the mean.



```{r}
r4s_fps %>% 
  data.frame() %>% 
  janitor::clean_names() %>% 
  rename(fp_rate = x) %>% 
  bind_cols(parameters) %>% 
  ggplot(.,aes(correlation, fp_rate)) + 
  geom_point(aes(color = n), 
             size = 2.5) + 
  scale_color_gradientn(colors = c(freenome_colors[1], freenome_colors[2], freenome_colors[3])) + 
  theme_classic() + 
  labs(title = "False alarm % for single assay R4S Like Rule", 
       subtitle = "Function of correlation and batches(n) used to set limits")
```














